---
title: "Generating Paper Figures for Glauninger, Bard, Wong Hickernell et al."
author: "Jared Bard"
output: html_document
---

# Setup
## libraries, colors, labels and functions
```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,message = FALSE, warning = FALSE)
knitr::asis_output("\U0394  \U2192")
library(tidyverse)
library(conflicted)
library(corrr)
library(cowplot)
library(readxl)
library(egg)
library(ggsignif)
library(ggrepel)
library(devtools)
#install_github("jabard89/cat.extras")
library(cat.extras) #has nicely formatted log scales
library(flextable)
library(patchwork)
library(zoo)
library(here)
`%!in%` = Negate(`%in%`)
conflicts_prefer(dplyr::filter)
github_dir <- here()

# set theme

theme_sedseq <- function(base_size=10) {
  theme_grey(base_size=base_size, base_family = "") %+replace%
    theme(panel.grid=element_blank(),
          axis.text = element_text(size = base_size),
          strip.text.x = element_text(size = base_size, margin = margin(t = 10)),
          strip.text.y = element_text(size = base_size, margin = margin(r = 10)),
          panel.background=element_blank(),
          axis.ticks=element_line(colour="grey20"),
          panel.border=element_rect(fill=NA),
          legend.background = element_blank(),
          legend.key.height = unit(3, "mm"),
          legend.key = element_blank(),
          strip.background = element_blank(),
          legend.box.spacing = unit(1, "mm"))
}
theme_set(theme_sedseq(base_size=10))

graycol <- "#333333cc"
orangecol <- "#cc5500cc"
bluecol <- "#0000aacc"
greencol <- "#22cc00cc"
purplecol <- "#cc22cccc"
cyancol <- "#2aa198cc"
redcol <- "#dc322fcc"
violetcol <- "#6c71c4cc"
blackcol <- "#000000cc"

okabe_ito_colors <- palette.colors(n = NULL, palette = "Okabe-Ito", recycle = FALSE)

stress.cols <-  c("30C"="#7F7F7F",
                  "42C"=RColorBrewer::brewer.pal(n=7,"Oranges")[4],
                  "46C"=RColorBrewer::brewer.pal(n=7,"Oranges")[6],
                  "mock"="#7F7F7F",
                  "Azide 0.5%"=RColorBrewer::brewer.pal(n=5,"Greens")[3],
                  "Azide 0.8%"=RColorBrewer::brewer.pal(n=5,"Greens")[5],
                  "Ethanol 5%"=RColorBrewer::brewer.pal(n=7,"Purples")[3],
                  "Ethanol 7.5%"=RColorBrewer::brewer.pal(n=7,"Purples")[5],
                  "Ethanol 10%"=RColorBrewer::brewer.pal(n=7,"Purples")[6],
                  "Ethanol 15%"=RColorBrewer::brewer.pal(n=7,"Purples")[7],
                  "DTT" = okabe_ito_colors[["reddishpurple"]])
stress.cols.darker <- c("30C"="#7F7F7F",
                  "42C"=RColorBrewer::brewer.pal(n=7,"Oranges")[4],
                  "46C"="red")
species.cols <- c("Scerevisiae"="#7F7F7F",
                  "Spombe"=purplecol)

induction.cols <- c("New"=purplecol,
                "Old"="grey20")

cat.cols <- c("down" = RColorBrewer::brewer.pal(12,"Paired")[10],
              "up" = RColorBrewer::brewer.pal(12,"Paired")[4])

target.cols <- c("HSF1 targets"= "#DDAA33",
                 "MSN2/4 targets"="#BB5566" )


stress_labs <- c("30C"="30°C","42C"="42°C","46C"="46°C","mock"="mock",
                 "Azide 0.5%"="0.5% Azide","Azide 0.8%"="0.8% Azide",
                 "Ethanol 5%"="5% EtOH","Ethanol 7.5%"="7.5% EtOH","Ethanol 10%"="10% EtOH","Ethanol 15%"="15% EtOH")


sg_enrichment_colors = c('enriched'=orangecol, 'depleted'=violetcol, 'neither'=graycol)
all_cols <- c(stress.cols,sg_enrichment_colors,graycol,orangecol,bluecol,greencol,purplecol,
              cyancol,redcol,violetcol,blackcol)
# make gimp palette

# Write to GPL file
gpl_file <- file.path(github_dir,"figures/RNA-condensation.gpl")

# Open the file for writing
con <- file(gpl_file, "w")

# Write the header and name
cat("GIMP Palette\n", file=con)
cat(paste("Name:", "RNA-condensation"), "\n", file=con)
# Convert hex codes to R G B format and write
for (i in 1:length(all_cols)) {
  col_rgb <- col2rgb(all_cols[i])
  cat(col_rgb[1], col_rgb[2], col_rgb[3], "   ", names(all_cols)[i], "\n", file=con)
}

# Close the connection
close(con)
# Shape and alpha for points
shap = 16
alph = 0.3

geom_cross <- function(data = NULL, grouping= NULL,
                       x = NULL, y = NULL, qmin = 0.25, qmax = 0.75, color = "black", ...){
  label <- sym(grouping)
  # Ensure x and y are specified
  if(is.null(x) | is.null(y)) {
    stop("Please specify x and y variables.")
  }
  
  # Calculate the cross data for each label group
  df_label_sum <- data %>% 
    group_by(!!label) %>% 
    summarise(
      x_med = median(!!sym(x), na.rm = TRUE),
      x_min = quantile(!!sym(x), qmin, na.rm = TRUE),
      x_max = quantile(!!sym(x), qmax, na.rm = TRUE),
      y_med = median(!!sym(y), na.rm = TRUE),
      y_min = quantile(!!sym(y), qmin, na.rm = TRUE),
      y_max = quantile(!!sym(y), qmax, na.rm = TRUE)
    )
  geoms <- list()
  
  for (label_val in unique(df_label_sum %>% pull(!!label))) {
    df_subset <- df_label_sum %>% filter(!!label == label_val)
    if (is.null(color)) {
      geoms <- append(geoms, list(
        geom_errorbar(inherit.aes = FALSE, data = df_subset,
                      aes(x = x_med, ymin = y_min, ymax = y_max,color=!!label),
                      width=0,
                      size = 1),
        geom_errorbar(inherit.aes = FALSE, data = df_subset,
                      aes(y = y_med, xmin = x_min, xmax = x_max,color=!!label),
                      width=0,
                      size = 1)
      ))
    }
    else {
      geoms <- append(geoms, list(
        geom_errorbar(inherit.aes = FALSE, data = df_subset,
                      aes(x = x_med, ymin = y_min, ymax = y_max),
                      color=color,
                      width=0,
                      size = 1),
        geom_errorbar(inherit.aes = FALSE, data = df_subset,
                      aes(y = y_med, xmin = x_min, xmax = x_max),
                      color=color,
                      width=0,
                      size = 1)
      ))
    }
  }
  return(geoms)
}

plot_density_x <- function(df,var,scale,min,max,cols,alph=0.5,siz=0.25,fill="top100"){
  X <- sym(var)
  fil <- sym(fill)
  if (scale%in%c("log2","log10")){
    p <- ggplot(df,aes(x=log10(!!X),fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(log10(min)-1,log10(max)+1))+
      coord_cartesian(xlim=c(log10(min),log10(max)),expand=F)
  } else{
    p <- ggplot(df,aes(x=!!X,fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(min-1,max+1))+
      coord_cartesian(xlim=c(min,max),expand=F)
  }
  return(p)
}

plot_density_y <- function(df,var,scale,min,max,cols,alph=0.5,siz=0.25,fill="top100"){
  X <- sym(var)
  fil <- sym(fill)
  if (scale%in%c("log2","log10")){
    p <- ggplot(df,aes(x=log10(!!X),fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      scale_x_continuous(limits=c(log10(min)-1,log10(max)+1))+
      theme_void()+
      guides(fill="none")+
      coord_flip(xlim=c(log10(min),log10(max)))
  } else{
    p <- ggplot(df,aes(x=!!X,fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(min-1,max+1))+
      coord_flip(xlim=c(min,max))
  }
  return(p)
}

# annotations

# annotations are built by src/annotations/label_genes.Rmd

gene_labels <- readr::read_tsv(file.path(github_dir,"src/annotations/labeled_genes_scer.tsv")) %>%
  dplyr::mutate(length.trans = LengthTxEst) %>%
  select(ORF,gene,classification,label,LengthTxEst,length.protein)

## load data

df_Zsup_Poly_minfilt <- read_tsv(file.path(github_dir,"data_processed/df_Zsup_Poly_minfilt_paper_figures.tsv.gz"))

df_samples_byLysate <- read_tsv(file.path(github_dir,
                                          "data_processed/RNAseq_samples_byLysate.tsv"))

df_stress_samples <- read_tsv(file.path(github_dir,
                                        "data_processed/stress_samples.tsv")) %>%
  mutate(Stress=factor(Stress,levels=c("none","Heat Shock","Azide","Azide pH4","Ethanol","Dextrose","DTT","KCl")),
         Stress_label=factor(Stress_label,levels=c("none","30C","42C","42CR","46C",
                                                   "mock","Azide 0.5%","Azide 0.8%",
                                                   "Ethanol 5%","Ethanol 7.5%","Ethanol 10%","Ethanol 15%",
                                                   "DTT 10mM","KCl 1M","withdrawal","Azide 0.5% pH4")))

df_Zsup_mean <- read_tsv(file.path(github_dir,
                                   "data_processed/sedseq_filt_mean.tsv.gz")) %>%
  left_join(df_samples_byLysate %>% select(Treatment_group,Treatment,Temperature,Time) %>% unique,by=c("Treatment","Treatment_group","Temperature"))

df_Occ_mean_minfilt <- read_tsv(file.path(github_dir,
                                          "data_processed/PolySeq_minfilt_mean.tsv.gz")) %>%
  left_join(df_stress_samples,by=c("Temperature","Treatment_group","Treatment")) %>%
  filter(!is.na(Control)) %>%
  group_by(Treatment_group,ORF) %>%
  filter(length(ORF[Control==TRUE])==1) %>%
  mutate(Occ.odds.FC = Occ.odds.mean/Occ.odds.mean[Control==TRUE])


df_Weinberg <- read_tsv(file.path(github_dir,"src/Weinberg_2016/weinberg_shah_synthesis_2016.txt"),
                       comment="#") %>%
  mutate(TE = TE/median(TE,na.rm=T)) %>%
  select(ORF,TE,pE)

muhl = read_tsv(file.path(github_dir,"src/Muhlhofer_2019/Muhlhofer_2019_rnaseq.tsv"), comment='#') |> pivot_wider(values_from = TPM, names_from=sample, names_prefix = 'tpm.')
```

```{r}
cutoff <- 0.05
df_vienna_utrs <- read_csv(file.path(github_dir,"RNAfold/Scerevisiae_UTR5plus20.csv"),
                          comment="#") %>%
  mutate(length_UTR5=str_length(UTR5),
         length_UTR5plus20=str_length(UTR5_plus20))
df_rnafold <- read_tsv(file.path(github_dir,"RNAfold/","ViennaFold_UTR5plus20.tsv")) %>% 
  left_join(df_vienna_utrs,by="ORF") %>%
  mutate(Energy_norm=Energy/length_UTR5plus20) %>%
  filter(!is.na(Energy)) %>%
  left_join(gene_labels %>% select(ORF,classification),by="ORF") %>%
  filter(classification=="Verified") %>%
  mutate(EnergyBin = case_when(Energy<=quantile(Energy,c(cutoff))~"most structured 5'UTR",
                                Energy>=quantile(Energy,c(1-cutoff))~"least structured 5'UTR",
                               TRUE~"other")) %>%
  mutate(EnergyBin=factor(EnergyBin,levels=c("least structured 5'UTR",
                                             "other",
                                             "most structured 5'UTR")))
```

# Figure 2

deltasedScore vs. RNA abundance, 42/46
```{r}
genes_to_lab <- c("SSB1","SSA4","HSP104","HSP26","PMU1","ADD66")
df <- df_Zsup_Poly_minfilt %>% filter(Stress_group=="Heat Shock",Temperature%in%c("42C","46C")) %>%
  mutate(target = if_else(str_detect(label,"HSF1"),"HSF1 targets",
                          if_else(str_detect(label,"MSN2"),"MSN2/4 targets","other"))) %>%
  mutate(target=factor(target,levels=c("other","MSN2/4 targets","HSF1 targets"))) %>%
  arrange(target) %>%
  mutate(gene_lab=if_else(gene%in%genes_to_lab,gene,""))
plot_hs <- function(df,xmin,xmax,ymin,ymax,xscale,xbreaks,yscale,ybreaks) {
  df <-  df %>%
    mutate(TPM.FC.SedSeq.plot = if_else(TPM.FC.SedSeq<xmin,xmin,
                                        if_else(TPM.FC.SedSeq>xmax,xmax,TPM.FC.SedSeq)),
           deltaZ.plot = if_else(deltaZ<ymin,ymin,
                               if_else(deltaZ>ymax,ymax,deltaZ)))
  p_scatter <- ggplot(df,aes(x=TPM.FC.SedSeq,y=deltaZ,color=target))+
    geom_hline(yintercept=0,linetype="dotted")+geom_vline(xintercept=1,linetype="dotted")+
    geom_point(data=df%>%filter(target=="other"),aes(x=TPM.FC.SedSeq.plot,y=deltaZ.plot),
               alpha=0.8,color="gray80",shape=16,size=0.8)+
    geom_point(data=df%>%filter(target!="other"),aes(x=TPM.FC.SedSeq.plot,y=deltaZ.plot),
               alpha=0.8,shape=16,size=1)+
    coord_cartesian(xlim=c(xmin,xmax),ylim=c(ymin,ymax),expand=F)+
    scale_color_manual(values=c("HSF1 targets"=unname(target.cols["HSF1 targets"]),
                                "MSN2/4 targets"=unname(target.cols["MSN2/4 targets"]),
                                "other"="black"))+
    geom_cross(data=df%>%filter(target%in%c("HSF1 targets")),grouping="target",x="TPM.FC.SedSeq",y="deltaZ")+
    geom_point(data=df%>%filter(gene%in%genes_to_lab),aes(x=TPM.FC.SedSeq.plot,y=deltaZ.plot),
               alpha=1,size=2,shape=16)
   if (xscale=="log2"){
    p_scatter <- p_scatter+scale_x_log2nice(omag=xbreaks)  
  } else if (xscale=="log10"){
    p_scatter <- p_scatter+scale_x_log10nice(omag=xbreaks)
  } else {
    p_scatter <- p_scatter+scale_x_continuous(breaks=xbreaks)
  }
  if (yscale=="log2"){
    p_scatter <- p_scatter+scale_y_log2nice(omag=ybreaks)  
  } else if (yscale=="log10"){
    p_scatter <- p_scatter+scale_y_log10nice(omag=ybreaks)
  } else {
    p_scatter <- p_scatter+scale_y_continuous(breaks=ybreaks)
  }
  
  # Overlay the density plots onto the main plot using annotation_custom
  p_combined <- p_scatter +
    geom_text_repel(aes(label=gene_lab),
                    max.overlaps = 10000,min.segment.length = 0,
                    size=8*0.35,color="black")+
    labs(x="",y="")+
    theme(plot.margin = margin(0, 0, 0, 0, "pt"))+
    theme(legend.position="nonoe")
}
p_42C <- plot_hs(df%>%filter(Temperature=="42C"), 0.5,60,-2.5,3.5,"log2",c(-2,0,2,4),"linear",c(-2,0,2))
p_42C
ggsave(file.path(github_dir,"figures/Figure2/42C_zoom.pdf"),egg::set_panel_size(p_42C,width=unit(50,"mm"),height=unit(50,"mm")),
       width=75,height=75,units="mm")
p_46C <- plot_hs(df%>%filter(Temperature=="46C"),0.4,8,-2.5,3.5,"log2",c(0,1,2),"linear",c(-2,0,2))+
  theme(axis.text.y=element_blank())
p_46C
ggsave(file.path(github_dir,"figures/Figure2/46C_zoom.pdf"),egg::set_panel_size(p_46C,width=unit(50,"mm"),height=unit(50,"mm")),
       width=75,height=75,units="mm",bg="transparent")
```

# Figure 3
## violins
```{r}
df_30_control <- df_Zsup_mean %>% filter(Treatment_group == "milderEtOH2", Temperature == "30C" & Treated == FALSE) %>% group_by( Temperature, Treated) %>% filter(SP.mean>0,!is.infinite(SP.mean)) %>% summarise(mean_sp_30 = mean(SP.mean)) 

df_30 <- df_Zsup_mean %>% filter (Temperature == "30C")  %>% filter(Treatment_group == "milderEtOH1") %>% filter(Treated == FALSE) %>%  left_join(df_30_control, by = c("Temperature", "Treated")) %>% select(-SP.mean) %>% rename(SP.mean = mean_sp_30) %>% mutate(Control=FALSE) 

df <- df_Zsup_mean %>%
  filter(Temperature!="42CR",
         Treatment!="KCl_1M") %>%
  filter(Treatment_group%in%c("EW_TSPP","Azide_0.5%_pH6.8","azide3",
                              "milderEtOH1","milderEtOH2","HyperOsmotic_EtOH")) %>%
  mutate(Control=case_when(Treatment_group=="EW_TSPP"&Temperature=="30C"~TRUE,
                           Treatment_group!="EW_TSPP"&Treated==FALSE~TRUE,
                           TRUE~FALSE)) %>%
  #filter(Temperature != "30C" | Treatment_group != "EW_TSPP") %>% 
  rbind(df_30) %>% 
  filter(SP.mean>0,!is.infinite(SP.mean)) %>%
  group_by(Treatment_group,ORF) %>%
  filter(length(ORF[Control==TRUE])==1) %>%
  mutate(SP.FC = SP.mean/SP.mean[Control==TRUE]) %>%
  #filter(Control==FALSE|(Treatment_group=="EW_TSPP"&Temperature=="30C")) %>%
  filter(Control == FALSE) %>% 
  mutate(Stress_label=case_when(Temperature%in%c("42C","46C")~Temperature,
                               # Treatment_group=="EW_TSPP"&Temperature=="30C"~"mock",
                               Treatment_group=="milderEtOH1"&Treatment=="mock"~"mock",
                                Treatment=="EtOH_15%"~"Ethanol 15%",
                                Treatment=="EtOH_10%"~"Ethanol 10%",
                                Treatment=="EtOH_7.5%"~"Ethanol 7.5%",
                                Treatment=="EtOH_5%"~"Ethanol 5%",
                                Treatment=="Azide_0.8%_pH6.8"~"Azide 0.8%",
                                Treatment=="Azide_0.5%_pH6.8"~"Azide 0.5%")) %>%
  mutate(Stress_label=factor(Stress_label,
                             levels=c("mock","42C","46C","Azide 0.5%","Azide 0.8%",
                                      "Ethanol 5%","Ethanol 7.5%","Ethanol 10%","Ethanol 15%"))) %>%
  filter(Stress_label%in%c("mock","42C","46C","Azide 0.5%","Azide 0.8%",
                           "Ethanol 7.5%","Ethanol 15%"))
stress_labels <- c("mock"="mock",
                   "42C"="42°C",
                   "46C"="46°C",
                   "Azide 0.5%"="0.5%",
                   "Azide 0.8%"="0.8%",
                   "Ethanol 5%"="5%",
                   "Ethanol 7.5%"="7.5%",
                   "Ethanol 10%"="10%",
                   "Ethanol 15%"="15%")
p_violin <- ggplot(df,
                   #%>%filter(Stress_label!="mock"),
       aes(x=Stress_label,y=SP.FC))+
  geom_hline(yintercept=1,linetype="dotted")+
  geom_point(shape=16,alpha=0.2,color="grey50",position=position_jitter(width=0.2), size = 0.5)+
  geom_violin(aes(fill=Stress_label,alpha=Stress_label))+
  geom_violin(fill=NA,alpha=1,draw_quantiles = c(0.5),size=0.5)+
  scale_y_log10nice()+
  scale_x_discrete(labels=stress_labels)+
  coord_cartesian(ylim=c(0.01,8))+
  scale_fill_manual(values=stress.cols)+
  scale_alpha_manual(values=c("mock"=0.8,
                   "42C"=0.8,
                   "46C"=0.8,
                   "Azide 0.5%"=0.8,
                   "Azide 0.8%"=0.8,
                   "Ethanol 5%"=0.8,
                   "Ethanol 7.5%"=0.8,
                   "Ethanol 10%"=0.8,
                   "Ethanol 15%"=0.7))+
  labs(y="",x="")
p_violin

ggsave("../figures/Figure3/all_violins.pdf",
       p_violin+theme(legend.position="none"),
       width=70,height=65,units="mm",bg="transparent")
```

```{r}

labeled_genes <- c("SSB1","SSA4")

plot_density_x <- function(df,var,scale,min,max,cols,alph=0.5,siz=0.25,fill="top100"){
  X <- sym(var)
  fil <- sym(fill)
  if (scale%in%c("log2","log10")){
    p <- ggplot(df,aes(x=log10(!!X),fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(log10(min)-1,log10(max)+1))+
      coord_cartesian(xlim=c(log10(min),log10(max)),expand=F)
  } else{
    p <- ggplot(df,aes(x=!!X,fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(min-1,max+1))+
      coord_cartesian(xlim=c(min,max),expand=F)
  }
  return(p)
}

plot_density_y <- function(df,var,scale,min,max,cols,alph=0.5,siz=0.25,fill="top100"){
  X <- sym(var)
  fil <- sym(fill)
  if (scale%in%c("log2","log10")){
    p <- ggplot(df,aes(x=log10(!!X),fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      scale_x_continuous(limits=c(log10(min)-1,log10(max)+1))+
      theme_void()+
      guides(fill="none")+
      coord_flip(xlim=c(log10(min),log10(max)))
  } else{
    p <- ggplot(df,aes(x=!!X,fill=!!fil))+
      geom_density(alpha=alph,size=siz)+
      scale_fill_manual(values=cols)+
      theme_void()+
      guides(fill="none")+
      scale_x_continuous(limits=c(min-1,max+1))+
      coord_flip(xlim=c(min,max))
  }
  return(p)
}

plot_fc_top100 <- function(df,xvar,yvar,
                           xmin,xmax,ymin,ymax,
                           xscale,xbreaks,yscale,ybreaks,
                           top100cat,col,genes_to_lab) {
  X <- sym(xvar)
  Y <- sym(yvar)
  top100cat <- sym(top100cat)
  df <- df %>% ungroup %>%
    mutate(top100 = if_else(!!top100cat>sort(!!top100cat,decreasing=TRUE)[101],TRUE,FALSE)) %>%
    mutate(top100=factor(top100,levels=c(FALSE,TRUE))) %>%
    mutate(gene_lab = if_else(gene%in%genes_to_lab,gene,NA_character_))
  xint <- ifelse (xscale%in%c("log2","log10"),1,0)
  yint <- ifelse (yscale%in%c("log2","log10"),1,0)
  p_scatter <- ggplot(df,
                      aes(x=!!X,y=!!Y,color=top100))+
    geom_hline(yintercept = yint,
               linetype = 'dashed') +
    geom_vline(xintercept = xint,
               linetype = 'dashed') +
    geom_point(data=df%>%filter(gene%!in%genes_to_lab,top100==FALSE),alpha=0.6,shape=16,size=0.4)+
    geom_point(data=df%>%filter(gene%!in%genes_to_lab,top100==TRUE),alpha=0.5,shape=16,size=0.5)+
    geom_point(data=df%>%filter(gene%in%genes_to_lab,top100==FALSE),alpha=1,shape=16,size=1.5,color="black")+
    geom_point(data=df%>%filter(gene%in%genes_to_lab,top100==TRUE),alpha=1,shape=16,size=1.5)+
    guides(color="none")+
    scale_color_manual(values=c("TRUE"=col, "FALSE"="grey"))+
    coord_cartesian(xlim=c(xmin,xmax),ylim=c(ymin,ymax),expand=F)+
    labs(x="",y="")+
    geom_cross(data=df%>%filter(top100==TRUE),grouping="top100",x=xvar,y=yvar,color = "black")+
    geom_text_repel(aes(label=gene_lab),size=8*0.35,min.segment.length = 0,color="black")
    geom_cross(data=df%>%filter(top100==TRUE),grouping="top100",x=xvar,y=yvar, color = "black")+
    geom_text_repel(aes(label=gene_lab),size=8*0.35,min.segment.length = 0.07,color="black")
  if (xscale=="log2"){
    p_scatter <- p_scatter+scale_x_log2nice(omag=xbreaks)  
  } else if (xscale=="log10"){
    p_scatter <- p_scatter+scale_x_log10nice(omag=xbreaks)
  } else {
    p_scatter <- p_scatter+scale_x_continuous(breaks=xbreaks)
  }
  if (yscale=="log2"){
    p_scatter <- p_scatter+scale_y_log2nice(omag=ybreaks)  
  } else if (yscale=="log10"){
    p_scatter <- p_scatter+scale_y_log10nice(omag=ybreaks)
  } else {
    p_scatter <- p_scatter+scale_y_continuous(breaks=ybreaks)
  }
  
  # For the density of x-axis
  x_density_bottom <- ifelse(yscale%in%c("log2","log10"),log10(ymin),ymin)
  x_density_top <- ifelse(yscale%in%c("log2","log10"),log10(ymin) + 0.3 * (log10(ymax)-log10(ymin)),ymin+0.3*(ymax-ymin))
  
  # For the densitx of y-axis
  y_density_left <- ifelse(xscale%in%c("log2","log10"),log10(xmin),xmin)
  y_density_right <- ifelse(xscale%in%c("log2","log10"),log10(xmin) + 0.3 * (log10(xmax)-log10(xmin)),xmin+0.3*(xmax-xmin))
  
  # Create density plots
  cols <- c("TRUE"=col, "FALSE"="grey")
  
  p_dens_x <- plot_density_x(df,xvar,xscale,xmin,xmax,cols)
  p_dens_y <- plot_density_y(df,yvar,yscale,ymin,ymax,cols)
  
  # Overlay the density plots onto the main plot using annotation_custom
  p_combined <- p_scatter +
    annotation_custom(grob = ggplotGrob(p_dens_x), 
                      xmin = ifelse(xscale%in%c("log2","log10"),log10(xmin),xmin),
                      xmax = ifelse(xscale%in%c("log2","log10"),log10(xmax),xmax), 
                      ymin = x_density_bottom, ymax = x_density_top)+
    annotation_custom(grob = ggplotGrob(p_dens_y), 
                      xmin = y_density_left, xmax = y_density_right,
                      ymin = ifelse(yscale%in%c("log2","log10"),log10(ymin),ymin),
                      ymax = ifelse(yscale%in%c("log2","log10"),log10(ymax),ymax))+
    labs(x="",y="")+
    theme(plot.margin = margin(0, 0, 0, 0, "pt"))
  return(p_combined)
}

p_42C_deltaZ_TPMFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="42C",Stress_group=="Heat Shock"),
                                     xvar="TPM.FC.SedSeq",yvar="deltaZ",
                                     xmin=0.1,xmax=500,ymin=(-4),ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["42C"]),genes_to_lab=labeled_genes)
p_42C_deltaZ_TPMFC_panel <- egg::set_panel_size(p=p_42C_deltaZ_TPMFC+
                                                  theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_42C_deltaZ_TPMFC_panel)


p_N3_deltaZ_TPMFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Azide 0.8%",Stress_group=="Azide 0.8%"),
                                     xvar="TPM.FC.SedSeq",yvar="deltaZ",
                                     xmin=0.1,xmax=500,ymin=(-4),ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["Azide 0.8%"]),genes_to_lab=labeled_genes)
p_N3_deltaZ_TPMFC_panel <- egg::set_panel_size(p=p_N3_deltaZ_TPMFC+
                                                 theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_N3_deltaZ_TPMFC_panel)

p_EtOH_deltaZ_TPMFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Ethanol 7.5%",Stress_group=="Ethanol 7.5%"),
                                     xvar="TPM.FC.SedSeq",yvar="deltaZ",
                                     xmin=0.1,xmax=500,ymin=(-4),ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["Ethanol 7.5%"]),genes_to_lab=labeled_genes)
p_EtOH_deltaZ_TPMFC_panel <- egg::set_panel_size(p=p_EtOH_deltaZ_TPMFC,width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_EtOH_deltaZ_TPMFC_panel)

p_deltaZ_TPMFC <- gtable_rbind(p_42C_deltaZ_TPMFC_panel,p_N3_deltaZ_TPMFC_panel,p_EtOH_deltaZ_TPMFC_panel)
ggsave("../figures/Figure3/deltaZ_TPMFC.pdf",p_deltaZ_TPMFC,bg="transparent")

### PolyFC vs TPMFC


p_42C_PolyFC_TPMFC <-  plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="42C",Stress_group=="Heat Shock"),
                                     xvar="TPM.FC.SedSeq",yvar="FC.vs.ctrl_TE",
                                     xmin=0.1,xmax=500,ymin=0.25,ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="log2",ybreaks=c(-1,0,1),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["42C"]),genes_to_lab=labeled_genes)
p_42C_PolyFC_TPMFC_panel <- egg::set_panel_size(p=p_42C_PolyFC_TPMFC+
                                                  theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))

p_N3_PolyFC_TPMFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Azide 0.8%",Stress_group=="Azide 0.8%"),
                                     xvar="TPM.FC.SedSeq",yvar="FC.vs.ctrl_TE",
                                     xmin=0.1,xmax=500,ymin=0.25,ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="log2",ybreaks=c(-1,0,1),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["Azide 0.8%"]),genes_to_lab=labeled_genes)
p_N3_PolyFC_TPMFC_panel <- egg::set_panel_size(p=p_N3_PolyFC_TPMFC+theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))

p_EtOH_PolyFC_TPMFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Ethanol 7.5%",Stress_group=="Ethanol 7.5%"),
                                     xvar="TPM.FC.SedSeq",yvar="FC.vs.ctrl_TE",
                                     xmin=0.1,xmax=500,ymin=0.25,ymax=4,
                                     xscale="log10",xbreaks=c(0,1,2),
                                     yscale="log2",ybreaks=c(-1,0,1),
                                     top100cat="TPM.FC.SedSeq",col=unname(stress.cols["Ethanol 7.5%"]),genes_to_lab=labeled_genes)
p_EtOH_PolyFC_TPMFC_panel <- egg::set_panel_size(p=p_EtOH_PolyFC_TPMFC,width=unit(25,"mm"),height=unit(25,"mm"))

p_PolyFC_TPMFC <- gtable_rbind(p_42C_PolyFC_TPMFC_panel,p_N3_PolyFC_TPMFC_panel,p_EtOH_PolyFC_TPMFC_panel)
ggsave("../figures/Figure3/PolyFC_TPMFC.pdf",p_PolyFC_TPMFC,bg="transparent")

### PolyFC vs deltaZ

p_42C_deltaZ_PolyFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="42C",Stress_group=="Heat Shock"),
                                     xvar="FC.vs.ctrl_TE",yvar="deltaZ",
                                     xmin=0.25,xmax=4,ymin=(-4.3),ymax=4.3,
                                     xscale="log2",xbreaks=c(-1,0,1),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="FC.vs.ctrl_TE",col=unname(stress.cols["42C"]),genes_to_lab=labeled_genes)
p_42C_deltaZ_PolyFC_panel <- egg::set_panel_size(p=p_42C_deltaZ_PolyFC+
                                                  theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_42C_deltaZ_PolyFC_panel)


p_N3_deltaZ_PolyFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Azide 0.8%",Stress_group=="Azide 0.8%"),
                                     xvar="FC.vs.ctrl_TE",yvar="deltaZ",
                                     xmin=0.25,xmax=4,ymin=(-4.3),ymax=4.3,
                                     xscale="log2",xbreaks=c(-1,0,1),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="FC.vs.ctrl_TE",col=unname(stress.cols["Azide 0.8%"]),genes_to_lab=labeled_genes)
p_N3_deltaZ_PolyFC_panel <- egg::set_panel_size(p=p_N3_deltaZ_PolyFC+
                                                 theme(axis.text.x=element_blank(),
                                                      axis.ticks.x=element_blank(),
                                                      plot.margin=margin(0,0,-11,0,unit="pt")),
                           width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_N3_deltaZ_PolyFC_panel)

p_EtOH_deltaZ_PolyFC <- plot_fc_top100(df=df_Zsup_Poly_minfilt %>% filter(Stress_label=="Ethanol 7.5%",Stress_group=="Ethanol 7.5%"),
                                     xvar="FC.vs.ctrl_TE",yvar="deltaZ",
                                     xmin=0.25,xmax=4,ymin=(-4.3),ymax=4.3,
                                     xscale="log2",xbreaks=c(-1,0,1),
                                     yscale="linear",ybreaks=c(-3,0,3),
                                     top100cat="FC.vs.ctrl_TE",col=unname(stress.cols["Ethanol 7.5%"]),genes_to_lab=labeled_genes)
p_EtOH_deltaZ_PolyFC_panel <- egg::set_panel_size(p=p_EtOH_deltaZ_PolyFC,width=unit(25,"mm"),height=unit(25,"mm"))
plot(p_EtOH_deltaZ_PolyFC_panel)
p_deltaZ_PolyFC <- gtable_rbind(p_42C_deltaZ_PolyFC_panel,p_N3_deltaZ_PolyFC_panel,p_EtOH_deltaZ_PolyFC_panel)
ggsave("../figures/Figure3/deltaZ_PolyFC.pdf",p_deltaZ_PolyFC,bg="transparent")

```


# Figure 5
## A: Occ vs Zsup

```{r}
set.seed(100)
df_hairpins <- df_Zsup_mean %>% filter(Treatment_group=="hairpinReporters") %>%
  group_by(ORF) %>%
  summarise(SP.mean = exp(mean(log(SP.mean))),
            Zsup.mean = mean(Zsup.mean),
            TPM.mean = exp(mean(log(Total.TPM.mean))))
df_30C_occ <- df_Occ_mean_minfilt %>%
  filter(Treatment%in%c("none","mock"),Temperature=="30C") %>%
  group_by(ORF) %>%
  summarise(Occ.odds.mean = exp(mean(log(Occ.odds.mean))))
df <- df_hairpins %>% full_join(df_30C_occ,by="ORF") %>%
  filter(!is.na(Zsup.mean),!is.na(Occ.odds.mean),!is.infinite(Occ.odds.mean),Occ.odds.mean>0) %>%
  left_join(gene_labels,by="ORF") %>%
  left_join(df_Weinberg,by="ORF") %>%
  filter(Occ.odds.mean>0) %>%
  left_join(df_rnafold %>%
              select(ORF,EnergyBin),by="ORF") %>%
  mutate(EnergyBin=if_else(EnergyBin=="uORF","other",EnergyBin)) %>%
  mutate(EnergyBin=factor(EnergyBin,levels=c("least structured 5'UTR","other","most structured 5'UTR"),
                          labels=c("least","other","most"))) %>% 
  arrange(EnergyBin)
df_corr <- df %>% 
  nest() %>%
  mutate(corr = map(data,function(df){
    df %>% column_to_rownames(var="ORF") %>% correlate(method="spearman")
  })) %>%
  select(-data) %>%
  unnest(corr) 
genes_to_label <- c("HAC1","GCN4")
energy_color_scale <- c("least" = RColorBrewer::brewer.pal(12,"Paired")[4], 
                              "other" = "grey50", 
                              "most" = RColorBrewer::brewer.pal(12,"Paired")[10])
p_Occ <- ggplot(df,
       aes(x=Occ.odds.mean,y=Zsup.mean))+
  geom_hline(yintercept=0,linetype="dotted")+
  geom_vline(xintercept=median(df$Occ.odds.mean,na.rm=T),linetype="dotted")+
  geom_point(data=df%>%filter(EnergyBin=="other"),alpha=0.5, shape = 16, size = 0.8, color = "grey")+
  geom_point(data=df%>%filter(EnergyBin!="other"),alpha=0.75,aes(color=EnergyBin), shape = 16, size = 0.8)+
  scale_color_manual(values=energy_color_scale)+
  #scale_x_log10nice()+#coord_cartesian(xlim=c(0.2,50))+
  scale_x_log10nice()+
  geom_text(data=df_corr %>% filter(term=="Occ.odds.mean"),
             aes(label=paste0("r = ",round(Zsup.mean,digits=2)),
                 x=1,y=2.8),
            size=10*0.35)+
  geom_smooth(method="lm",se=F,color="black")+
  #geom_point(data=df %>% filter(gene%in%genes_to_label),size=2,color="red")+
  #geom_label_repel(data=df %>% filter(gene%in%genes_to_label),size=4.2,aes(label=gene))+
  labs(x="",y="")+
  theme(legend.position="none")
p_Occ
p_zsup_box <- ggplot(df %>% filter(!is.na(EnergyBin)),
         aes(x=EnergyBin,y=Zsup.mean,fill=EnergyBin))+
    geom_point(position=position_jitterdodge(jitter.width=1.5),
               aes(color=EnergyBin,alpha=EnergyBin), shape =16, size = 0.75)+
  scale_color_manual(values=energy_color_scale)+
    scale_alpha_manual(values=c("least" = 0.6, "other" = 0.1, "most" = 0.6)) +
  geom_violin(fill=NA,draw_quantiles = c(0.5),size=0.5,color="black")+
    theme(legend.position="none")+
  ggsignif::geom_signif(na.rm=T,
                        map_signif_level=T,
                        test="wilcox.test",
              y_position=c(2,2),
              textsize = 4.2,
              comparisons=list(
                c("least","other"),
                c("other","most")
              ))+
  labs(x="",y="")+
  theme(axis.text.x = element_text(angle=45,hjust=1))
p_zsup_box
ggsave("../figures/Figure5/Zsup_Occ_left.pdf",
       egg::set_panel_size(p=p_Occ,width=unit(30,"mm"),height=unit(30,"mm")),
       width=75,height=75,units="mm",bg="transparent")
ggsave("../figures/Figure5/Zsup_Occ_right.pdf",
       egg::set_panel_size(p=p_zsup_box+theme(axis.title.y=element_blank()),width=unit(30,"mm"),height=unit(30,"mm")),
       width=75,height=75,units="mm",bg="transparent")
```


```{r}
genes_to_label <- c("HAC1","GCN4")

df_hairpins <- df_Zsup_mean %>% filter(Treatment_group=="hairpinReporters") %>%
  group_by(ORF) %>%
  summarise(SP.mean = exp(mean(log(SP.mean))),
            Zsup.mean = mean(Zsup.mean),
            TPM.mean = exp(mean(log(Total.TPM.mean))))
df_30C_occ <- df_Occ_mean_minfilt %>%
  filter(Treatment%in%c("none","mock"),Temperature=="30C") %>%
  group_by(ORF) %>%
  summarise(Occ.odds.mean = exp(mean(log(Occ.odds.mean))))
df <- df_hairpins %>% full_join(df_30C_occ,by="ORF") %>%
  left_join(gene_labels,by="ORF") %>%
  left_join(df_Weinberg,by="ORF") %>%
  filter(Occ.odds.mean>0) %>%
  mutate(gene_label = if_else(gene%in%genes_to_label,gene,""))
df_corr <- df %>% ungroup %>%
  nest() %>%
  mutate(corr = map(data,function(df){
    df %>% select(ORF,Zsup.mean,TE,Occ.odds.mean,TPM.mean) %>% column_to_rownames(var="ORF") %>% correlate(method="spearman")
  })) %>%
  select(-data) %>%
  unnest(corr) 
p_TPM_TE <- ggplot(df,
       aes(x=TPM.mean,y=TE))+
  scale_x_log10nice()+coord_cartesian(xlim=c(1,1e4))+
  scale_y_log10nice()+coord_cartesian(ylim=c(0.01,10))+
  geom_point(alpha=0.3, size = 0.5, shape = 16, color = "black", )+
  geom_point(data=df %>% filter(gene%in%genes_to_label),size=2,color="red")+
  geom_text_repel(data=df,size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0)+
  labs(x="mRNA Abundance",y="Translation\nEfficiency")
p_TPM_TE

p_Z_box <- ggplot(df,
                  aes(x=1,y=Zsup.mean))+
  geom_point(data=df%>%filter(gene%!in%genes_to_label),position=position_jitter(width=0.43),alpha=0.02, size = 0.3)+
  #geom_boxplot(fill=NA,outlier.shape=NA)+
  geom_violin(fill="grey70", alpha = 0.6, draw_quantiles = c(0.5))+
  geom_point(data=df%>%filter(gene%in%genes_to_label),alpha=1,color="red",size=1)+
  #geom_text_repel(data=df%>%filter(gene=="GCN4"),size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0,nudge_y=2.5,nudge_x=0.25)+
  #geom_text_repel(data=df%>%filter(gene=="HAC1"),size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0,nudge_y=-2.5 ,nudge_x=0.25)+
  labs(x="",y="Zsup")+
  theme(axis.title.x=element_blank(),  # Removes x-axis label
        axis.text.x=element_blank(),   # Removes x-axis tick labels
        axis.ticks.x=element_blank(),   # Removes x-axis ticks
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
        )
p_Z_box
ggsave("../figures/Figure5/TPM_TE_left.pdf",
       egg::set_panel_size(p=p_TPM_TE+labs(x="",y=""),width=unit(30,"mm"),height=unit(30,"mm")),
       width=100,height=100,units="mm",bg="transparent")
ggsave("../figures/Figure5/TPM_TE_right.pdf",egg::set_panel_size(p=p_Z_box+labs(x="",y=""),width=unit(15,"mm"),height=unit(30,"mm")),
       width=100,height=100,units="mm",bg="transparent")
```

# Supplemental

```{r}
df_sedseq_withreps <- read_tsv(file.path(github_dir,
                                   "data_processed/sedseq_out.tsv.gz")) %>%
  left_join(df_samples_byLysate %>% select(Treatment_group,Treatment,Temperature,Time) %>%
              unique,by=c("Treatment","Treatment_group","Temperature","Time")) %>%
  left_join(df_stress_samples,by=c("Temperature","Treatment_group","Treatment")) %>%
  filter(!is.na(Control))
df <- df_sedseq_withreps %>%
  left_join(gene_labels,by="ORF") %>%
  filter(classification=="Verified") %>%
  select(ORF,Dataset,Strain,Treatment_group,Treatment_group_ID,Stress,Stress_group,Stress_label,Treatment,Temperature,Biorep,Zsup) %>%
  pivot_wider(names_from=Biorep,values_from=Zsup) %>%
  filter(Stress_group %in% c("Heat Shock","Azide 0.5%","Azide 0.8%",
                             "Ethanol 5%","Ethanol 7.5%","Ethanol 10%","Ethanol 15%")) %>%
  filter(Temperature!="42CR") %>%
  arrange(Stress,Treatment_group_ID,Stress_label) %>%
  mutate(facet_col = interaction(Stress_label,Treatment_group_ID))
 
# Step 1: Compute the correlation matrix. Here's an example with more variables.
# If you're only comparing BR1 and BR2 directly, adjust this step accordingly.
df_cor <- df %>%
  group_by(Stress,Stress_label,Treatment_group,Treatment_group_ID,Treatment,facet_col) %>%
  summarize(pearson = cor(BR1, BR2, method = "pearson",use="pairwise.complete.obs"))

stress_label_mapping <- df %>%
  distinct(Stress_label,facet_col) %>% unique %>%
  pull(Stress_label,name=facet_col)
stress_facet_labeller <- function(value) {
  mapped_label <- stress_label_mapping[value]
  return(mapped_label)
}
plot_table <- df %>%
  group_by(Stress,Treatment_group_ID) %>%
  nest %>%
  mutate(plot = pmap(list("df"=data,"stress_var"=Stress,"tg"=Treatment_group_ID),function(df,stress_var,tg){
    df_cor_filt <- df_cor %>% filter(Stress==stress_var,Treatment_group_ID==tg)
    ggplot(data = df, aes(x = BR1, y = BR2)) +
    geom_hline(yintercept = 0, color = "grey",linetype="dotted") +
    geom_vline(xintercept = 0, color = "grey",linetype="dotted") +
    geom_point(size = 0.5, shape=16,alpha=0.5,color="grey",na.rm = TRUE) +
    coord_cartesian(xlim = c(-5, 5), ylim = c(-5, 5)) +
    scale_x_continuous(breaks = c(-4, 0, 4)) +
    scale_y_continuous(breaks = c(-4, 0, 4)) +
    geom_smooth(method = "lm", formula = "y ~ x", se = FALSE, na.rm = TRUE,
                color = "black", size = 0.25) +
    geom_text(label = "r =", x = -4, y = 4, hjust = 0,
              size = 8*0.35, color = "black") +
    geom_text(data=df_cor_filt,inherit.aes=F,aes(label = sprintf("%.2f", pearson)),
              x = -4, y = 2, hjust = 0,
              size = 8*0.35, color = "black") +
    theme_sedseq(base_size=8) +
    theme(aspect.ratio = 1)+
       theme(axis.title.x = element_blank(),
             axis.text.x = element_blank(),
             axis.title.y = element_blank(),
             axis.text.y = element_blank())+
      facet_grid(.~facet_col,labeller=as_labeller(stress_facet_labeller))
  }))
p_out_HS <- plot_table %>% filter(Stress=="Heat Shock") %>% pull(plot) %>% .[[1]]
p_out_N3_tg20 <- plot_table %>% filter(Stress=="Azide",Treatment_group_ID=="tg_20") %>% pull(plot) %>% .[[1]]
p_out_N3_tg9 <- plot_table %>% filter(Stress=="Azide",Treatment_group_ID=="tg_9") %>% pull(plot) %>% .[[1]]
p_out_EtOH_tg10 <- plot_table %>% filter(Stress=="Ethanol",Treatment_group_ID=="tg_10") %>% pull(plot) %>% .[[1]]
p_out_EtOH_tg11 <- plot_table %>% filter(Stress=="Ethanol",Treatment_group_ID=="tg_11") %>% pull(plot) %>% .[[1]]
p_out_EtOH_tg12 <- plot_table %>% filter(Stress=="Ethanol",Treatment_group_ID=="tg_12") %>% pull(plot) %>% .[[1]]

ggsave("../figures/Supplemental/compare_Zsup_bioreps_HS.pdf",
       egg::set_panel_size(p=p_out_HS,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
ggsave("../figures/Supplemental/compare_Zsup_bioreps_N3_tg20.pdf",
       egg::set_panel_size(p=p_out_N3_tg20,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
ggsave("../figures/Supplemental/compare_Zsup_bioreps_N3_tg9.pdf",
       egg::set_panel_size(p=p_out_N3_tg9,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
ggsave("../figures/Supplemental/compare_Zsup_bioreps_EtOH_tg10.pdf",
       egg::set_panel_size(p=p_out_EtOH_tg10,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
ggsave("../figures/Supplemental/compare_Zsup_bioreps_EtOH_tg11.pdf",
       egg::set_panel_size(p=p_out_EtOH_tg11,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
ggsave("../figures/Supplemental/compare_Zsup_bioreps_EtOH_tg12.pdf",
       egg::set_panel_size(p=p_out_EtOH_tg12,width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg="transparent")
```

## noise hairpin replicates
```{r}

odds <- function(p) {
  p/(1-p)
}
logodds <- function(x) {
  # log odds, a shortcut
  res <- log(odds(x))
  res[!is.finite(res)] <- NA
  res
}
rollup <- function(x, flds, name, ...) {
  y <- zoo(x[,flds])
  res <- as.data.frame(rollapply(zoo(x[,flds]),...))
  colnames(res) <- paste(name,flds,sep='.')
  as_tibble(res) %>% mutate(ORF=x$ORF)
}
df <- df_Zsup_mean %>%
  filter(Treatment_group == "hairpinReporters",
         pSup.mean>0,SP.mean>0,!is.infinite(pSup.mean),!is.infinite(SP.mean)) %>%
  left_join(gene_labels %>% select(ORF,gene,classification),by="ORF") %>%
  filter(classification=="Verified") %>%
  group_by(ORF,gene,LengthTxEst) %>%
  summarise(SP.mean.all = exp(mean(log(SP.mean))),
         SP.sem.all = exp(sd(log(SP.mean))/sqrt(n()))) %>%
  mutate(lo.psup = log(SP.mean.all)) %>%
  ungroup %>% nest %>%
  mutate(data=map(data,function(df){
    binwidth <- 100
    min.binwidth <- 5 # For edges
    roll.mean.SP <- rollup(df%>%arrange(LengthTxEst), c('SP.mean.all'), "mean", width=binwidth, FUN=mean,
                        by.column=TRUE, na.rm=TRUE, fill=NA, partial=min.binwidth)
    roll.lo.mean <- rollup(df%>%arrange(LengthTxEst),
                           c('lo.psup'), "mean",width=binwidth, FUN=mean, by.column=TRUE, na.rm=TRUE, fill=NA, partial=min.binwidth)
    roll.sd <- rollup(df%>%arrange(LengthTxEst),
                      c('lo.psup'), "sd",width=binwidth, FUN=sd, by.column=TRUE, na.rm=TRUE, fill=NA, partial=min.binwidth)
    return(df %>% full_join(roll.mean.SP,by="ORF") %>%
             full_join(roll.lo.mean,by="ORF") %>%
             full_join(roll.sd,by="ORF") )
  })) %>% unnest(data) %>%
  mutate(Zsup = (lo.psup-mean.lo.psup)/sd.lo.psup)
# not bad set.seed(1)
set.seed(1)
which_genes <- df_Zsup_mean %>%
  filter(Treatment_group == "hairpinReporters",
         pSup.mean>0,SP.mean>0,!is.infinite(pSup.mean),!is.infinite(SP.mean)) %>%
  group_by(ORF) %>%
  summarise(Total.TPM = exp(mean(log(Total.TPM.mean))),
            zSup.mean = mean(Zsup.mean)) %>%
  left_join(gene_labels,by="ORF") %>%
  filter(!is.na(gene),classification=="Verified",
         LengthTxEst < 6e3,LengthTxEst > 300) %>%
  ungroup %>%
  mutate(zSup_group = if_else(zSup.mean>=0,"zSup.up","zSup.down")) %>%
  mutate(length_bin = cut_interval(log(LengthTxEst),n=6)) %>%
  group_by(length_bin,zSup_group) %>%
  nest %>%
  mutate(sampled = map(data,function(df) {
    return(tibble(sampled_genes = sample(df$gene,size=1)))
  })) %>%
  select(-data) %>%
  unnest(sampled)

genes_to_highlight <- which_genes$sampled_genes
genes_to_label <- c("GCN4","HAC1")


set_label_size = theme(
  axis.title.x = element_text(size = 10),
  axis.text.x = element_text(size = 10),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 10))
p <- ggplot(df,
            aes(x=LengthTxEst,y=SP.mean.all))+
  geom_point(alpha=0.3,shape=16,size=0.5,color="grey60")+
  geom_line(aes(y=mean.SP.mean.all),color="black",size=0.5,alpha=0.5,linetype=1,linewidth=0.5)+
  geom_line(aes(y=exp(mean.lo.psup-sd.lo.psup)),color=okabe_ito_colors[["bluishgreen"]],size=1,linewidth=0.5, linetype=1)+
  geom_line(aes(y=exp(mean.lo.psup+sd.lo.psup)),color=okabe_ito_colors[["bluishgreen"]],size=1, linewidth=0.5, linetype=1)+
  scale_x_log10nice()+ scale_y_log10nice()+
  coord_cartesian(ylim=c(0.5,40))+
  geom_point(data=df %>% filter(gene %in% c(genes_to_highlight)),
             size=1.5,shape=16)+
  geom_errorbar(data=df %>% filter(gene %in% c(genes_to_highlight)),
             aes(y=SP.mean.all,
                 ymin=SP.mean.all-SP.sem.all,
                 ymax=SP.mean.all+SP.sem.all),
             width=0,linewidth=1)+
  geom_point(data=df %>% filter(gene=="GCN4"),
             size=1.5,shape=16,
                  color=okabe_ito_colors[["vermillion"]])+
  geom_errorbar(data=df %>% filter(gene=="GCN4"),
             aes(y=SP.mean.all,
                 ymin=SP.mean.all-SP.sem.all,
                 ymax=SP.mean.all+SP.sem.all),
             width=0,linewidth=1,
                  color=okabe_ito_colors[["vermillion"]])+
  geom_point(data=df %>% filter(gene=="HAC1"),
             size=1.5,shape=16,
                  color=stress.cols[["DTT"]])+
  geom_errorbar(data=df %>% filter(gene=="HAC1"),
             aes(y=SP.mean.all,
                 ymin=SP.mean.all-SP.sem.all,
                 ymax=SP.mean.all+SP.sem.all),
             width=0,linewidth=1,
                  color=stress.cols[["DTT"]])+
  geom_label_repel(data=df%>%filter(gene=="HAC1"),
                  aes(label=gene),
                  size=0.35*8,
                  nudge_x = -0.4, nudge_y = -0.4,
                  linewidth=0.25,
                  color=stress.cols[["DTT"]])+
  geom_label_repel(data=df%>%filter(gene=="GCN4"),
                  aes(label=gene),
                  size=0.35*8,
                  nudge_x = 0.4, nudge_y = 0.4,
                  linewidth=0.25,
                  color=okabe_ito_colors[["vermillion"]])+
  set_label_size+
  labs(x="mRNA length (nucleotides)", y="Odds in supernatant")
p

ggsave("../figures/Supplemental/hairpin_30C_error.pdf",
        egg::set_panel_size(p=p,
                            width=unit(50,"mm"),height=unit(50,"mm")),
       width=75,height=75,units="mm",bg = "transparent",dpi=600)
```

## hac1 equiv
```{r}
rollup <- function(x, flds, name, ...) {
  y <- zoo(x[,flds])
  res <- as.data.frame(rollapply(zoo(x[,flds]),...))
  colnames(res) <- paste(name,flds,sep='.')
  as_tibble(res) %>% mutate(ORF=x$ORF)
}
df <- df_Zsup_mean %>% filter(Treatment_group=="EW_TSPP",
                              Temperature%in%c("30C"),
                              ORF!="YBL111C") %>%
  group_by(Temperature) %>%
  nest %>%
  mutate(data=map(data,function(df){
    df <- df %>% filter(pSup.mean>0,SP.mean>0,!is.infinite(pSup.mean),!is.infinite(SP.mean))
    binwidth <- 100
    min.binwidth <- 5 # For edges
    roll.mean <- rollup(df%>%arrange(LengthTxEst), c('pSup.mean'), "mean", width=binwidth, FUN=mean,
                        by.column=TRUE, na.rm=TRUE, fill=NA, partial=min.binwidth)
    roll.mean.SP <- rollup(df%>%arrange(LengthTxEst), c('SP.mean'), "mean", width=binwidth, FUN=mean,
                        by.column=TRUE, na.rm=TRUE, fill=NA, partial=min.binwidth)
    return(df%>%full_join(roll.mean,by="ORF") %>% full_join(roll.mean.SP,by="ORF"))
  })) %>% unnest(data) %>%
  left_join(gene_labels %>% select(ORF,gene),by="ORF")
hac1_30C_SP <- df %>% filter(ORF=="YFL031W") %>% pull(SP.mean)
hac1_30C_equiv_length <- df %>%
  mutate(diff = abs(hac1_30C_SP-mean.SP.mean)) %>%
  arrange(diff) %>% 
  slice(1) %>% pull(LengthTxEst)
hac1_length <- gene_labels %>% filter(ORF=="YFL031W") %>% pull(LengthTxEst)
p_SP <- ggplot(df %>% filter(!is.infinite(SP.mean),SP.mean>0),
            aes(x=LengthTxEst,y=SP.mean))+
  geom_point(alpha=0.2,shape=16, size= 0.3,color="grey50")+
  geom_line(aes(y=mean.SP.mean,group=Temperature),color="black",size=0.5)+
  scale_x_log10nice()+scale_y_log10nice()+
  coord_cartesian(ylim=c(0.05,80))+
  geom_segment(aes(x=hac1_length,y=hac1_30C_SP,xend=hac1_30C_equiv_length,yend=hac1_30C_SP),
               linetype="dotted",color="black")+
  geom_segment(aes(x=hac1_30C_equiv_length,y=1e-10,xend=hac1_30C_equiv_length,yend=hac1_30C_SP),
               linetype="dotted",color="black")+
  geom_point(data=df%>%filter(ORF=="YFL031W"),color=stress.cols[["DTT"]],size=2)+
  labs(x="",y="")+
  theme(legend.position="none")
p_SP
ggsave("../figures/Supplemental/HAC1_equiv_length.pdf",
       egg::set_panel_size(p=p_SP,
                           width=unit(40,"mm"),height=unit(40,"mm")),
       width=75,height=75,units="mm",bg = "transparent",dpi=600)
```

## zsup 30 vs 42 hsf1
```{r}
genes_to_lab <- c("SSA4")
upper<-4.7
lower<-(-4.7)
df <- df_Zsup_mean %>% filter(Treatment_group=="EW_TSPP") %>%
  select(ORF,Temperature,Zsup.mean) %>%
  left_join(gene_labels,by="ORF") %>%
  pivot_wider(names_from=Temperature,values_from=Zsup.mean,names_prefix="Zsup.") %>%
  mutate(target = if_else(label=="HSF1","HSF1 targets","other")) %>%
  mutate(target=factor(target,levels=c("other","MSN2/4 targets","HSF1 targets"))) %>%
  arrange(target) %>%
  mutate(Zsup.30C=case_when(Zsup.30C>upper~upper,
                            Zsup.30C<lower~lower,
                            TRUE~Zsup.30C),
         Zsup.42C=case_when(Zsup.42C>upper~upper,
                            Zsup.42C<lower~lower,
                            TRUE~Zsup.42C)) %>%
  mutate(gene_lab = if_else(gene%in%genes_to_lab,gene,""))
df_corr <- df %>%
  correlate(method="pearson")
corr <- (df_corr %>% filter(term=="Zsup.30C") %>% pull(Zsup.42C))^2
p_zsup <- ggplot(df,
       aes(x=Zsup.30C,y=Zsup.42C))+
  geom_abline(slope=1,linetype="dotted")+
  geom_point(data=df%>%filter(target=="other"),alpha=0.2,shape=16,color="grey50", size = 0.5)+
  geom_point(data=df%>%filter(target!="other"),aes(color=target),size=0.8,shape=16,alph=0.3)+
  scale_x_continuous(breaks=c(-4,0,4))+scale_y_continuous(breaks=c(-4,0,4))+
  scale_color_manual(values=target.cols)+
  coord_cartesian(xlim=c(lower,upper),ylim=c(lower,upper),expand=F)+
  theme(legend.position = "none")+
  # geom_text(data=df_corr%>%filter(term=="Zsup.30C"),
  #      aes(x=-3,y=3,label=paste0("r^2=",round(Zsup.42C^2,digits=2))),
  #      size=12*0.35)+
  labs(x="",y="")
p_zsup
ggsave("../figures/Supplemental/Zsup.pdf",
       egg::set_panel_size(p=p_zsup,width=unit(30,"mm"),height=unit(30,"mm")),
       bg="transparent",width=50,height=50,units="mm")

p_zsup_46C <- ggplot(df,
       aes(x=Zsup.30C,y=Zsup.46C))+
  geom_abline(slope=1,linetype="dotted")+
  geom_point(data=df%>%filter(target=="other"),alpha=0.2,shape=16,color="grey50", size = 0.5)+
  geom_point(data=df%>%filter(target!="other"),aes(color=target),size=0.8,shape=16,alph=0.3)+
  scale_x_continuous(breaks=c(-4,0,4))+scale_y_continuous(breaks=c(-4,0,4))+
  scale_color_manual(values=target.cols)+
  coord_cartesian(xlim=c(lower,upper),ylim=c(lower,upper),expand=F)+
  theme(legend.position = "none")+
  # geom_text(data=df_corr%>%filter(term=="Zsup.30C"),
  #      aes(x=-3,y=3,label=paste0("r^2=",round(Zsup.42C^2,digits=2))),
  #      size=12*0.35)+
  labs(x="",y="")
p_zsup_46C
ggsave("../figures/Supplemental/Zsup_30vs46.pdf",
       egg::set_panel_size(p=p_zsup_46C,width=unit(30,"mm"),height=unit(30,"mm")),
       bg="transparent",width=50,height=50,units="mm")
```
```{r}
upper<-7.5 
lower<-(-4.7)
df <- df_Zsup_mean %>% filter(Treatment_group=="EW_TSPP") %>%
  select(ORF,Temperature,Zsup.mean) %>%
  left_join(gene_labels,by="ORF") %>%
  mutate(target = if_else(label=="HSF1","HSF1 targets","other")) %>%
  mutate(target=factor(target,levels=c("other","MSN2/4 targets","HSF1 targets"))) %>%
  arrange(target) %>%
  ungroup %>%
  mutate(deltaZ = Zsup.mean-Zsup.mean[Temperature=="30C"]) %>%
  mutate(deltaZ.trimmed =case_when(deltaZ>upper~upper,
                            deltaZ<lower~lower,
                            TRUE~deltaZ)) %>%
  mutate(gene_lab = if_else(gene%in%genes_to_lab,gene,"")) %>%
  filter(Temperature %in% c("42C","46C"))

p_zsup_boxes <- ggplot(df,
       aes(x=target,y=deltaZ))+
  geom_hline(yintercept=0,linetype="dotted")+
    geom_point(position=position_jitterdodge(jitter.width=1.5),
               aes(y=deltaZ.trimmed,color=target),shape=16,alpha=0.5, size = 0.5)+
  scale_color_manual(values=target.cols)+
  geom_violin(fill=NA,draw_quantiles = c(0.5),size=0.25,color="black")+
    theme(legend.position="none")+
  coord_cartesian(y=c(lower,upper))+
  ggsignif::geom_signif(na.rm=T,
                        map_signif_level=T,
                        test="wilcox.test",
              y_position=c(5.5),
              textsize = 4.2,
              comparisons=list(
                c("other","HSF1 targets")
              ))+
  labs(x="",y="")+
  facet_grid(.~Temperature)+
  theme(axis.text.x = element_blank(),
        strip.text.x = element_blank())
p_zsup_boxes
ggsave("../figures/Supplemental/Zsup_hsf1_boxplot.pdf",
       egg::set_panel_size(p=p_zsup_boxes,width=unit(30,"mm"),height=unit(30,"mm")),
       bg="transparent",width=100,height=50,units="mm")

wilcox_result <- df %>%
  group_by(Temperature) %>%
  nest %>%
  mutate(wilcox = map(data,function(df){
    wilcox.test(deltaZ ~ target, data = df, 
                             subset = (target %in% c("other", "HSF1 targets")),
                             exact = FALSE, # Use this for large samples
                             paired = FALSE # Set TRUE if the data are paired
    )
  }))
print(wilcox_result$wilcox)
```

## specificity bars
```{r}
df_long <- df_Zsup_Poly_minfilt %>% filter(Stress_group%in%c("Heat Shock","Ethanol 7.5%","Azide 0.8%"),
                                           Stress_label%in%c("42C","Ethanol 7.5%","Azide 0.8%")) %>%
  filter(!is.infinite(SP.FC),SP.FC>0) %>%
  group_by(Stress_label) %>%
  mutate(top100 = if_else(TPM.FC.SedSeq>sort(TPM.FC.SedSeq,decreasing=TRUE)[101],TRUE,FALSE)) %>%
  mutate(top100=factor(top100,levels=c(FALSE,TRUE))) %>%
  group_by(ORF) %>%
  mutate(stress_specific = if_else(length(ORF[top100==TRUE])==1&top100==TRUE,Stress_label,"none"))
df_specific <- df_long %>% select(ORF,stress_specific) %>% filter(stress_specific!="none")
df <- df_long %>% ungroup %>%
  select(-stress_specific) %>%
  left_join(df_specific,by="ORF") %>%
  replace_na(list(stress_specific="none")) %>%
  mutate(stress_specific = factor(stress_specific,levels=c("none","42C","Azide 0.8%","Ethanol 7.5%"))) %>%
  arrange(stress_specific)
df_wilcox <- df %>%
  group_by(Stress_group,Stress_label) %>%
  nest %>%
  mutate(p_value = map(data,function(df){
    pairwise_results <- pairwise.wilcox.test(df$deltaZ, df$stress_specific, p.adjust.method = "bonferroni")
    broom::tidy(pairwise_results)
  })) %>%
  select(-data) %>%
  unnest(p_value) %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(p_label = map(p.value,function(x){
    symnum(x, corr = FALSE, 
                 cutpoints = c(0, .001, .01, .05, 1), 
                 symbols = c("***", "**", "*", "N.S."))
  })) %>%
  unnest(p_label) %>%
  filter(group2 == "none") %>%
  rename("stress_specific" = "group1")
xend_adjust = c(-0.1,0.1,0.25)
annotation_df <- df_wilcox %>%
  add_column(x_start = c(rep(1,3),rep(2,3),rep(3,3)) - 0.25,
             x_end = c(1+xend_adjust,2 + xend_adjust, 3 + xend_adjust),
             y_pos = rep(c(3.1,3.7,4.3),3)) %>%
  mutate(id = row_number())

p_spec <- ggplot(df,
       aes(x=Stress_label,y=deltaZ,fill=stress_specific))+
  geom_hline(yintercept=0,linetype="dotted")+
  geom_point(aes(group=interaction(Stress_label,stress_specific),alpha=stress_specific),
                 shape=16,color="black",position=position_jitterdodge(jitter.width = 0.2,
                                                                                dodge.width = 0.75), size = 0.5)+
  scale_alpha_manual(values=c("none"=0.3,"42C"=0.3,"Azide 0.8%"=0.3,"Ethanol 7.5%"=0.3))+
  ggnewscale::new_scale_color() +
  # geom_violin(alpha=0.5)+
  # geom_violin(aes(group=interaction(Stress_label,stress_specific)),
  #             fill=NA,draw_quantiles = c(0.25,0.5,0.75),size=0.5)+
  geom_boxplot(outlier.shape=NA,alpha=0.5)+
  geom_boxplot(outlier.shape=NA,fill=NA,aes(group=interaction(Stress_label,stress_specific)),size=0.5)+
  scale_x_discrete(labels=c("42C"="42°C","Azide 0.8%"="0.8%\nAzide","Ethanol 7.5%"="7.5%\nEthanol"))+
  labs(x="",y="")+
  scale_fill_manual(values=stress.cols)+
  coord_cartesian(ylim=c(-3,4.5))+
  theme(legend.position = "none")+
  ggsignif::geom_signif(
    annotations = annotation_df$p_label,
    xmin = annotation_df$x_start,
    xmax = annotation_df$x_end,
    y_position = annotation_df$y_pos,
    textsize = 8*0.35,tip_length = 0,size=0.5
  )
p_spec
ggsave(file.path(github_dir,"figures/Supplemental/specific_boxplots.pdf"),
       egg::set_panel_size(p=p_spec,width=unit(70,"mm"),height=unit(50,"mm")),
       width=100,height=100,units="mm",bg="transparent",dpi=600)

```

## Khong N3
```{r}
kho = read_tsv(file.path(github_dir,"src/khong-parker-2017-yeast-sg-transcriptome-tableS2.txt"), comment='#')

pskho = df_Zsup_Poly_minfilt %>% filter(Stress_group=="Azide 0.8%") %>%
  left_join(kho %>% select(-gene), by='ORF') %>%
  mutate(Stress_label=factor(Stress_label,levels=c("mock","Azide 0.8%")))

gene_to_lab <- c("SOL4", "SPI1", "HSP42", "HXT6", "ARO10", "TPO2", "NRG1", "SDP1", "HSP30", "IRC15", "USV1", "CTA1", "GIP2", "GAS2")

khong_induced <- ggplot(pskho %>% filter(Stress_label == "Azide 0.8%"),
       aes(x = LengthTxEst, y = 1/foldchange.sg.total, colour = sg.classification)) + 
  geom_point(shape = shap, alpha = 0.5, size = 0.3) + 
  scale_loglog()+
  scale_colour_manual(values = sg_enrichment_colors) +
  geom_point(data = pskho %>% 
               filter(Stress_label == "Azide 0.8%" & gene %in% gene_to_lab), 
             aes(x = LengthTxEst, y = 1/foldchange.sg.total), 
             shape = 16, size = 1, color = "black")+
  geom_point(data = pskho %>% 
               filter(Stress_label == "Azide 0.8%" & gene %in% gene_to_lab), 
             aes(x = LengthTxEst, y = 1/foldchange.sg.total), 
             shape = 16, size = 0.5, color = "white")+
    guides(colour = guide_legend(override.aes = list(alpha = 1)))+
   theme(panel.spacing.x = grid::unit(0, "mm"),
        strip.placement = "outside",
        strip.background = element_blank(),
        aspect.ratio = 1) +
  labs(x="",y="")+
  theme(legend.position = "none")

ggsave("../figures/Supplemental/khong_induced.pdf",
        egg::set_panel_size(p=khong_induced,width=unit(20,"mm"),height=unit(20,"mm")),
       width=100,height=100,units="mm",bg="transparent")
khong_induced
```

## Pombe
```{r}
pombe_labels <- read_tsv(file.path(github_dir,"src","annotations","SPombe","Schizosaccharomyces_pombe_230503_gene_IDs_names_products_lengths.tsv"))
combined_labels <- pombe_labels %>%
  filter(gene_type=="protein coding gene") %>%
  select(ORF,LengthTxEst) %>% mutate(Species="Spombe") %>%
  bind_rows(gene_labels %>% filter(classification=="Verified") %>%
              select(ORF,LengthTxEst) %>% mutate(Species="Scerevisiae"))
df <- read_tsv(file.path(github_dir,"data_processed","pSup_spombe_spikeIn.tsv.gz")) %>%
  left_join(df_samples_byLysate,by="Lysate_sample") %>%
  filter(est_counts.Total>50) %>%
  group_by(ORF,Temperature) %>%
  summarise(SP.mean = mean(exp(log(SP)))) %>%
  mutate(pSup.mean = SP.mean/(1+SP.mean)) %>%
  left_join(combined_labels,by="ORF") %>%
  filter(!is.na(LengthTxEst)) %>%
  mutate(Species=factor(Species,levels=c("Scerevisiae","Spombe"))) %>%
  arrange(Species)
p <- ggplot(data = df %>% filter(!is.na(Species)),
       aes(x = LengthTxEst, y = SP.mean, color = Species, group = Species)) +
 geom_point(alpha=0.3,shape=16, size= 0.5)+
  geom_smooth(se = FALSE, size = 1, method = "glm",
              method.args = list(family = "binomial"), color = 'black',
              aes(linetype=Species)) +
  scale_x_log10nice() +
  #scale_y_continuous() +
  scale_y_log10nice(omag=c(-1,0,1))+
  coord_cartesian(ylim=c(0.05,100))+
  scale_linetype_manual(values= c('Spombe' = "11",
                              'Scerevisiae' = "solid"),
                     labels= c('Spombe' = 'S. pombe',
                              'Scerevisiae' = 'S. cerevisiae')) +
  scale_color_manual(values=species.cols)+
  theme(panel.spacing.x = grid::unit(0, "mm"),
        strip.placement = "outside",
        strip.background = element_blank(),
        aspect.ratio = 1) +
  facet_grid(rows = vars(Temperature),
             labeller = labeller(Temperature = c('30C' = '30°C',
                                                 '46C' = '46°C')))+
  labs(x="",y="")
p

ggsave("../figures/Supplemental/species_comp.pdf",
       egg::set_panel_size(p=p+theme(legend.position="none"),
                           width=unit(25,"mm"),height=unit(25,"mm")),
       width=50,height=100,units="mm",bg = "transparent")
```

```{r}

df <- df_Zsup_mean %>%
  filter(Temperature!="42CR",
         Treatment!="KCl_1M") %>%
  filter(Treatment_group%in%c("EW_TSPP","Azide_0.5%_pH6.8","azide3","milderEtOH1","milderEtOH2","HyperOsmotic_EtOH")) %>%
  mutate(Control=case_when(Treatment_group=="EW_TSPP"&Temperature=="30C"~TRUE,
                           Treatment_group!="EW_TSPP"&Treated==FALSE~TRUE,
                           TRUE~FALSE)) %>%
  filter(SP.mean>0,!is.infinite(SP.mean)) %>%
  group_by(Treatment_group,ORF) %>%
  filter(length(ORF[Control==TRUE])==1) %>%
  mutate(SP.FC = SP.mean/SP.mean[Control==TRUE]) %>%
  filter(Control==FALSE|(Treatment_group=="EW_TSPP"&Temperature=="30C")) %>%
  mutate(Stress_label=case_when(Temperature%in%c("42C","46C")~Temperature,
                                Treatment_group=="EW_TSPP"&Temperature=="30C"~"mock",
                                Treatment=="EtOH_15%"~"Ethanol 15%",
                                Treatment=="EtOH_10%"~"Ethanol 10%",
                                Treatment=="EtOH_7.5%"~"Ethanol 7.5%",
                                Treatment=="EtOH_5%"~"Ethanol 5%",
                                Treatment=="Azide_0.8%_pH6.8"~"Azide 0.8%",
                                Treatment=="Azide_0.5%_pH6.8"~"Azide 0.5%")) %>%
  mutate(Stress_label=factor(Stress_label,
                             levels=c("mock","42C","46C","Azide 0.5%","Azide 0.8%",
                                      "Ethanol 5%","Ethanol 7.5%","Ethanol 10%","Ethanol 15%"))) %>%
  filter(Stress_label != "mock")
stress_labels <- c("mock"="mock",
                   "42C"="42°C",
                   "46C"="46°C",
                   "Azide 0.5%"="0.5%",
                   "Azide 0.8%"="0.8%",
                   "Ethanol 5%"="5%",
                   "Ethanol 7.5%"="7.5%",
                   "Ethanol 10%"="10%",
                   "Ethanol 15%"="15%")

p_length_hs <- ggplot(df %>% filter(Stress_label %in% c("42C", "46C")),
                   aes(x=LengthTxEst,y=SP.FC,color=Stress_label))+
  geom_hline(yintercept=1,linetype="dotted")+
  geom_point(alpha=0.2, shape = 16, size = 0.3)+
  scale_color_manual(values=stress.cols)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labels))+
  scale_x_log10nice()+scale_y_log10nice()+
  geom_smooth(method="lm",se=F,na.rm=T,color="black")+
  coord_cartesian(ylim=c(0.005,2.5),xlim=c(200,20000))+
  theme(panel.spacing.x = grid::unit(0, "mm"),
        strip.placement = "outside",
        strip.background = element_blank(),
        aspect.ratio = 1)+
  theme(legend.position = "none")+
  labs(y="",x="")
p_length_hs

p_length_N3 <- ggplot(df %>% filter(Stress_label %in% c("Azide 0.5%", "Azide 0.8%")),
                   aes(x=LengthTxEst,y=SP.FC,color=Stress_label))+
  geom_hline(yintercept=1,linetype="dotted")+
  geom_point(alpha=0.2, shape = 16, size = 0.3)+
  scale_color_manual(values=stress.cols)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labels))+
  scale_x_log10nice()+scale_y_log10nice()+
  geom_smooth(method="lm",se=F,na.rm=T,color="black")+
  coord_cartesian(ylim=c(0.005,2.5),xlim=c(200,20000))+
  theme(panel.spacing.x = grid::unit(0, "mm"),
        strip.placement = "outside",
        strip.background = element_blank(),
        aspect.ratio = 1)+
  theme(legend.position = "none")+
  labs(y="",x="")
p_length_N3

p_length_EtOH <- ggplot(df %>% filter(Stress_label %in% c("Ethanol 5%", "Ethanol 7.5%",
                                                          "Ethanol 10%","Ethanol 15%")),
                   aes(x=LengthTxEst,y=SP.FC,color=Stress_label))+
  geom_hline(yintercept=1,linetype="dotted")+
  geom_point(alpha=0.2, shape = 16, size = 0.3)+
  scale_color_manual(values=stress.cols)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labels))+
  scale_x_log10nice()+scale_y_log10nice()+
  geom_smooth(method="lm",se=F,na.rm=T,color="black")+
  coord_cartesian(ylim=c(0.005,2.5),xlim=c(200,20000))+
  theme(panel.spacing.x = grid::unit(0, "mm"),
        strip.placement = "outside",
        strip.background = element_blank(),
        aspect.ratio = 1)+
  theme(legend.position = "none")+
  labs(y="",x="")
p_length_EtOH

ggsave("../figures/Supplemental/length_dep_HS.pdf",
        egg::set_panel_size(p=p_length_hs+theme(strip.text.x = element_blank(),
                                                axis.ticks.x = element_blank(),
                                                axis.text.x = element_blank()),
                            width=unit(15,"mm"),height=unit(15,"mm")),
       width=50,height=50,units="mm",bg = "transparent")


ggsave("../figures/Supplemental/length_dep_N3.pdf",
        egg::set_panel_size(p=p_length_N3+theme(strip.text.x = element_blank(),
                                                axis.ticks.x = element_blank(),
                                                axis.text.x = element_blank()),
                            width=unit(15,"mm"),height=unit(15,"mm")),
       width=50,height=50,units="mm",bg = "transparent")


ggsave("../figures/Supplemental/length_dep_EtOH.pdf",
        egg::set_panel_size(p=p_length_EtOH+theme(strip.text.x = element_blank()),
                            width=unit(15,"mm"),height=unit(15,"mm")),
       width=100,height=50,units="mm",bg = "transparent")
```

## Muhlhofer
```{r}
# Muhlhofer 2019 data
upr_targets = read_tsv(file.path(github_dir,"src/Kimata_2006/uprHac1pTargets.txt"), comment='#')
colnames(upr_targets) = c('gene','regulation','ORF')

df_muhl_fc <- muhl %>%
  pivot_longer(cols=c(-ORF),names_to="Treatment",values_to="TPM") %>%
  left_join(gene_labels,by="ORF") %>%
  filter(classification=="Verified") %>%
  # renorm the TPMs
  group_by(Treatment) %>%
  mutate(TPM = TPM*(sum(TPM,na.rm=T)/1e6)) %>%
  mutate(Treatment=str_replace(Treatment,"tpm.",""),
         Treatment = str_replace(Treatment,".Rep","~Rep")) %>%
  separate(Treatment,into=c("Treatment","Rep"),sep="~") %>%
  group_by(ORF,Treatment) %>%
  summarise(TPM.mean = exp(mean(log(TPM)))) %>%
  group_by(ORF) %>%
  mutate(TPM.FC = TPM.mean/TPM.mean[Treatment=="25C.control"]) %>%
  filter(TPM.FC > 0,!is.na(TPM.FC),!is.infinite(TPM.FC)) %>%
  mutate(Category = if_else(ORF %in% upr_targets$ORF,"UPR","other"))
muhlw = muhl |> mutate(
  fc37.10.r1=tpm.37C.10min.Rep1/tpm.25C.control.Rep1,
  fc37.10.r2=tpm.37C.10min.Rep2/tpm.25C.control.Rep2,
  fc37.30.r1=tpm.37C.30min.Rep1/tpm.25C.control.Rep1,
  fc37.30.r2=tpm.37C.30min.Rep2/tpm.25C.control.Rep2,
  fc42.10.r1=tpm.42C.10min.Rep1/tpm.25C.control.Rep1,
  fc42.10.r2=tpm.42C.10min.Rep2/tpm.25C.control.Rep2,
  fc42.30.r1=tpm.42C.30min.Rep1/tpm.25C.control.Rep1,
  fc42.30.r2=tpm.42C.30min.Rep2/tpm.25C.control.Rep2,
  fc37.10 = (fc37.10.r1+fc37.10.r2)/2,
  fc37.30 = (fc37.30.r1+fc37.30.r2)/2,
  fc42.10 = (fc42.10.r1+fc42.10.r2)/2,
  fc42.30 = (fc42.30.r1+fc42.30.r2)/2)

muhlfc = muhlw |> select(ORF, fc37.10,fc37.30,fc42.10,fc42.30) |> pivot_longer(cols=c(fc37.10,fc37.30,fc42.10,fc42.30), values_to="FC", names_to="Treatment", names_transform = function(x){substring(x,3,7)})

#muhl_fcs = c('fc37.10.r1','fc37.10.r2','fc37.30.r1','fc37.30.r2','fc42.10.r1','fc42.10.r2','fc42.30.r1','fc42.30.r2')
muhl_fcs = c('fc37.10','fc37.30','fc42.10','fc42.30')
muhl_treatments = c('37.10','37.30','42.10','42.30')

# P values for upregulation: Muhlhofer
upr_upreg = sapply(muhl_treatments, function(treat){
  x = muhlfc |> filter(Treatment==treat); 
  test = wilcox.test(unlist(x |> filter(ORF %in% upr_targets$ORF) |> select(FC)), unlist(x |> filter(!(ORF %in% upr_targets$ORF)) |> select(FC)), alternative = "greater")
  test
}, simplify=FALSE)
upr_p_values = sapply(upr_upreg, function(x){x$p.value})

# Effect sizes for UPR upregulation
upr_upreg_fc = sapply(muhl_treatments, function(treat){
  x = muhlfc |> filter(Treatment==treat); 
  median(unlist(x |> filter(ORF %in% upr_targets$ORF) |> select(FC)), na.rm=T)-median(unlist(x |> filter(!(ORF %in% upr_targets$ORF)) |> select(FC)), na.rm=T)
}, simplify=FALSE)
gmu = ggplot(muhlfc, aes(x=FC)) + stat_ecdf() + 
  stat_ecdf(data=muhlfc |> filter(ORF %in% upr_targets$ORF), colour='red') + 
  facet_grid(Treatment~.) + scale_x_log2nice(limits=c(0.25,4)) + 
  xlab("Fold change mRNA") + ylab("Cumulative distribution")
print(gmu)

df_muhl_upr_wilcox <- df_muhl_fc %>%
  mutate(Treatment = factor(Treatment,levels=c("25C.control","37C.10min","37C.30min","42C.10min","42C.30min"))) %>%
  arrange(Treatment) %>%
  filter(Treatment != "25C.control") %>%
  group_by(Treatment) %>%
  nest %>%
  mutate(wilcox = map(data,function(df){
    wilcox.test(TPM.FC ~ Category, data = df, 
                             exact = FALSE, # Use this for large samples
                             paired = FALSE, # Set TRUE if the data are paired
    )
  })) %>%
  mutate(p.wilcox = map_dbl(wilcox, ~ .x$p.value)) %>%
  mutate(p_label = map_chr(p.wilcox,function(x){
    symnum(x, corr = FALSE, 
                 cutpoints = c(0, .001, .01, .05, 1), 
                 symbols = c("***", "**", "*", "N.S."))
  }))

df <- df_muhl_fc %>%
  mutate(Treatment = factor(Treatment,levels=c("25C.control","37C.10min","37C.30min","42C.10min","42C.30min"))) %>%
  arrange(Treatment) %>%
  mutate(grouping_var = interaction(Treatment,Category,sep="~"))
p_violin = ggplot(df %>% filter(Treatment!="25C.control"),
                  aes(x=Treatment,y=TPM.FC,fill=Category,group=grouping_var)) +
  geom_hline(yintercept=1,linetype="dotted")+
  scale_y_log10nice()+
  geom_point(position=position_jitterdodge(jitter.width=0.2,dodge.width = 0.9),shape=16,alpha=0.3,color="grey50")+
  geom_violin(size=0.25,color="black",alpha=0.5,position=position_dodge(width=0.9))+
  geom_violin(fill=NA,draw_quantiles = c(0.25,0.5,0.75),,size=0.25,color="black",position=position_dodge(width=0.9))+
  coord_cartesian(ylim=c(1e-2,1e3))+
  scale_fill_manual(values=c("other"="grey50","UPR"=stress.cols[["DTT"]]))+
  ggsignif::geom_signif(
    annotations=df_muhl_upr_wilcox$p_label,
    y_position=rep(2.5,4),
    xmin = c(1,2,3,4)-0.225,
    xmax = c(1,2,3,4)+0.225,
    textsize = 10*0.35)
print(p_violin)

ggsave("../figures/Supplemental/Muhlhofer_upr.pdf",
        egg::set_panel_size(p=p_violin+theme(legend.position="none")+
                              labs(x="",y="")+
                              theme(axis.text.x = element_blank()),
                            width=unit(50,"mm"),height=unit(40,"mm")),
       width=100,height=100,units="mm",bg = "transparent",dpi=600)
```

## FC plots boxes
```{r}
df <- df_Zsup_Poly_minfilt %>% 
  filter(Control == FALSE) %>%
  filter(Stress_group=="Heat Shock"&Temperature%in%c("30C","42C","46C")|
           Stress_group=="Ethanol 7.5%" | 
           Stress_group == "Azide 0.8%") %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(Induction_cat = case_when(TPM.FC.SedSeq < quantile(TPM.FC.SedSeq,0.1) ~ "down",
                                   TPM.FC.SedSeq > quantile(TPM.FC.SedSeq,0.9) ~ "up",
                                   TRUE ~ "other"))

df_wilcox <- df %>%
  group_by(Stress_group,Stress_label) %>%
  nest %>%
  mutate(p_value = map(data,function(df){
    pairwise_results <- pairwise.wilcox.test(df$deltaZ, df$Induction_cat, p.adjust.method = "bonferroni")
    broom::tidy(pairwise_results)
  })) %>%
  select(-data) %>%
  unnest(p_value) %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(p_label = map(p.value,function(x){
    symnum(x, corr = FALSE, 
                 cutpoints = c(0, .001, .01, .05, 1), 
                 symbols = c("***", "**", "*", "N.S."))
  })) %>%
  unnest(p_label) %>%
  filter((group1 == "other" & group2 == "down") | 
           (group1 == "up" & group2 == "other"))

annotation_df <- df_wilcox %>%
  add_column(x_start = c(1,2,1,2,1,2,1,2),
             x_end = c(2,3,2,3,2,3,2,3),
             y_pos = rep(3,8)) %>%
  mutate(id = row_number())
p_box <- ggplot(df,
                aes(x=Induction_cat,y=deltaZ,fill=Stress_label))+
  geom_hline(yintercept=0,linetype="dotted")+
  geom_point(shape=16,alpha=0.5,size=0.5,color="grey50",
             position=position_jitter(width=0.2,seed=1))+
  geom_boxplot(outlier.shape=NA,alpha=0.5,size=0.5)+
  geom_boxplot(fill=NA,outlier.shape=NA,size=0.5)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labs))+
  scale_fill_manual(values=stress.cols)+
  labs(x="",y="")+
  coord_cartesian(ylim=c(-4,4))+
  scale_y_continuous(breaks=c(-3,0,3))+
  guides(fill="none")+
  ggsignif::geom_signif(
    manual = T,
    data = annotation_df,
    aes(xmin = x_start, xmax = x_end, annotations = p_label, y_position = y_pos, group = id),
    textsize = 8*0.35
  )
p_box
ggsave("../figures/Supplemental/FC_comp_deltaZ_induction_box.pdf",
       egg::set_panel_size(p_box,width=unit(30,"mm"),height=unit(30,"mm")),
       width=300,height=75,units="mm",bg="transparent",dpi=600)
```

```{r}
df <- df_Zsup_Poly_minfilt %>% 
  filter(Control == FALSE) %>%
  filter(Stress_group=="Heat Shock"&Temperature%in%c("30C","42C","46C")|
           Stress_group=="Ethanol 7.5%" | 
           Stress_group == "Azide 0.8%") %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(Induction_cat = case_when(TPM.FC.SedSeq < quantile(TPM.FC.SedSeq,0.1) ~ "down",
                                   TPM.FC.SedSeq > quantile(TPM.FC.SedSeq,0.9) ~ "up",
                                   TRUE ~ "other"))

df_wilcox <- df %>%
  group_by(Stress_group,Stress_label) %>%
  nest %>%
  mutate(p_value = map(data,function(df){
    pairwise_results <- pairwise.wilcox.test(df$FC.vs.ctrl_TE, df$Induction_cat, p.adjust.method = "bonferroni")
    broom::tidy(pairwise_results)
  })) %>%
  select(-data) %>%
  unnest(p_value) %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(p_label = map(p.value,function(x){
    symnum(x, corr = FALSE, 
                 cutpoints = c(0, .001, .01, .05, 1), 
                 symbols = c("***", "**", "*", "N.S."))
  })) %>%
  unnest(p_label) %>%
  filter((group1 == "other" & group2 == "down") | 
           (group1 == "up" & group2 == "other"))

annotation_df <- df_wilcox %>%
  add_column(x_start = c(1,2,1,2,1,2,1,2),
             x_end = c(2,3,2,3,2,3,2,3),
             y_pos = rep(0.5,8))%>%
  mutate(id = row_number())
p_box <- ggplot(df,
                aes(x=Induction_cat,y=FC.vs.ctrl_TE,fill=Stress_label))+
  geom_hline(yintercept=1,linetype="dotted")+
  geom_point(shape=16,alpha=0.5,size=0.5,color="grey50",
             position=position_jitter(width=0.2,seed=1))+
  geom_boxplot(outlier.shape=NA,alpha=0.5,size=0.5)+
  geom_boxplot(fill=NA,outlier.shape=NA,size=0.5)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labs))+
  scale_fill_manual(values=stress.cols)+
  labs(x="",y="")+
  scale_y_log2nice(omag=c(-1,0,1))+
  coord_cartesian(ylim=c(0.25,4))+
  guides(fill="none")+
  ggsignif::geom_signif(
    manual = T,
    data = annotation_df,
    aes(xmin = x_start, xmax = x_end, annotations = p_label, y_position = y_pos, group = id),
    textsize = 8*0.35
  )
p_box
ggsave("../figures/Supplemental/FC_comp_FCTE_induction_box.pdf",
       egg::set_panel_size(p_box,width=unit(30,"mm"),height=unit(30,"mm")),
       width=300,height=75,units="mm",bg="transparent",dpi=600)
```

```{r}
df <- df_Zsup_Poly_minfilt %>% 
  filter(Control == FALSE) %>%
  filter(Stress_group=="Heat Shock"&Temperature%in%c("30C","42C","46C")|
           Stress_group=="Ethanol 7.5%" | 
           Stress_group == "Azide 0.8%") %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(TE_cat = case_when(FC.vs.ctrl_TE < quantile(FC.vs.ctrl_TE,0.1) ~ "down",
                                   FC.vs.ctrl_TE > quantile(FC.vs.ctrl_TE,0.9) ~ "up",
                                   TRUE ~ "other"))

df_wilcox <- df %>%
  group_by(Stress_group,Stress_label) %>%
  nest %>%
  mutate(p_value = map(data,function(df){
    pairwise_results <- pairwise.wilcox.test(df$deltaZ, df$TE_cat, p.adjust.method = "bonferroni")
    broom::tidy(pairwise_results)
  })) %>%
  select(-data) %>%
  unnest(p_value) %>%
  group_by(Stress_group,Stress_label) %>%
  mutate(p_label = map(p.value,function(x){
    symnum(x, corr = FALSE, 
                 cutpoints = c(0, .001, .01, .05, 1), 
                 symbols = c("***", "**", "*", "N.S."))
  })) %>%
  unnest(p_label) %>%
  filter((group1 == "other" & group2 == "down") | 
           (group1 == "up" & group2 == "other"))

annotation_df <- df_wilcox %>%
  add_column(x_start = c(1,2,1,2,1,2,1,2),
             x_end = c(2,3,2,3,2,3,2,3),
             y_pos = rep(3,8)) %>%
  mutate(id = row_number())
p_box <- ggplot(df,
                aes(x=TE_cat,y=deltaZ,fill=Stress_label))+
  geom_hline(yintercept=0,linetype="dotted")+
  geom_point(shape=16,alpha=0.5,size=0.5,color="grey50",
             position=position_jitter(width=0.2,seed=1))+
  geom_boxplot(outlier.shape=NA,alpha=0.5,size=0.5)+
  geom_boxplot(fill=NA,outlier.shape=NA,size=0.5)+
  facet_grid(.~Stress_label,
             labeller=labeller(Stress_label=stress_labs))+
  scale_fill_manual(values=stress.cols)+
  labs(x="",y="")+
  coord_cartesian(ylim=c(-4,4))+
  scale_y_continuous(breaks=c(-3,0,3))+
  guides(fill="none")+
  ggsignif::geom_signif(
    manual = T,
    data = annotation_df,
    aes(xmin = x_start, xmax = x_end, annotations = p_label, y_position = y_pos, group = id),
    textsize = 8*0.35
  )
p_box
ggsave("../figures/Supplemental/FC_comp_FCTE_deltaZ_box.pdf",
       egg::set_panel_size(p_box,width=unit(30,"mm"),height=unit(30,"mm")),
       width=300,height=75,units="mm",bg="transparent",dpi=600)
```

### reporter supp figures
```{r}
set_label_size = theme(
  axis.title.x = element_text(size = 10),
  axis.text.x = element_text(size = 8),
  axis.title.y = element_text(size = 10),
  axis.text.y = element_text(size = 8))

df_pSup <- read_tsv(file.path(github_dir,"data_processed/230329-reporters-42C-20min.tsv")) %>%
  mutate(Experiment_group="42C") %>%
  mutate(Group=case_when(Probe!="YONL"~"native",
                         UTR5=="PMU1"&Reporter_age=="New"~"PMU1_New",
                         UTR5=="PMU1"&Reporter_age=="Old"~"PMU1_Old",
                         UTR5=="HSP26"&Reporter_age=="New"~"HSP26_New",
                         UTR5=="HSP26"&Reporter_age=="Old"~"HSP26_Old")) %>%
  mutate(Group = factor(Group,levels=c("native","HSP26_Old","HSP26_New","PMU1_Old","PMU1_New"))) %>%
  mutate(Skip=if_else(Probe=="PMU1"&UTR5=="PMU1",TRUE,FALSE)) %>%
  filter(Skip!=TRUE) %>%
  pivot_longer(cols=c(EDTA.FALSE,EDTA.TRUE),names_to="EDTA",values_to="pSup",names_prefix = "EDTA.") %>%
  mutate(SP = pSup/(1-pSup)) %>%
  mutate(EDTA = factor(EDTA,levels=c("TRUE","FALSE")))
df_Occ <- read_tsv(file.path(github_dir,"data_processed/230329-reporters-42C-20min.tsv")) %>%
  mutate(Experiment_group="42C") %>%
  mutate(Group=case_when(Probe!="YONL"~"native",
                         UTR5=="PMU1"&Reporter_age=="New"~"PMU1_New",
                         UTR5=="PMU1"&Reporter_age=="Old"~"PMU1_Old",
                         UTR5=="HSP26"&Reporter_age=="New"~"HSP26_New",
                         UTR5=="HSP26"&Reporter_age=="Old"~"HSP26_Old")) %>%
  mutate(Group = factor(Group,levels=c("native","HSP26_Old","HSP26_New","PMU1_Old","PMU1_New"))) %>%
  mutate(Skip=if_else(Probe=="PMU1"&UTR5=="PMU1",TRUE,FALSE)) %>%
  filter(Skip!=TRUE)

df_pSup_mean <- df_pSup %>%
  group_by(Experiment_group,Group,Probe,Temperature,EDTA) %>%
  summarise(SP.mean = exp(mean(log(SP),na.rm=T)),
            pSup.mean = mean(pSup)) %>%
  separate(Group,into=c("UTR5","Reporter_age"),remove=F)
df_Occ_mean <- df_Occ %>%
  group_by(Experiment_group,Group,Probe,Temperature) %>%
  summarise(Occ.mean = mean(Occupancy_corr)) %>%
  separate(Group,into=c("UTR5","Reporter_age"),remove=F)

p_native_pSup <- ggplot(df_pSup %>% filter(Group=="native") %>% filter(Probe != "TUB2"),
                        aes(x=Probe,y=1-pSup,color=Temperature, shape = Probe))+
   geom_col(data=df_pSup_mean %>% filter(Group == "native") %>% filter(Probe != "TUB2") ,
                aes(y=1-pSup.mean,ymin=1-pSup.mean,ymax=1-pSup.mean, fill = Temperature), position = "dodge", alpha = 0.25)+
  geom_point()+
  scale_color_manual(values=stress.cols)+
  facet_grid(Temperature~EDTA)+
  scale_fill_manual(values = stress.cols)+
  scale_shape_manual(values=c("PMU1"=16,"HSP26"=2))+
  coord_cartesian(ylim=c(0,1))
p_native_pSup

ggsave("../figures/Supplemental/Sucrose_native_pPel.pdf",
        egg::set_panel_size(p=p_native_pSup+labs(x="",y="")+set_label_size+
                              theme(legend.position="none",
                                    strip.text.x = element_blank()),
                            width=unit(30,"mm"),height=unit(30,"mm")),
       width=100,height=100,units="mm",bg = "transparent",dpi=600)
p_native_Occ <- ggplot(df_Occ %>% filter(Group=="native") %>% filter(Probe != "TUB2"),
                        aes(x=Probe,y=Occupancy_corr,color=Temperature, shape = Probe))+
  geom_col(data=df_Occ_mean %>% filter(Group == "native") %>% filter(Probe != "TUB2"),
                aes(y=Occ.mean,ymin=Occ.mean,ymax=Occ.mean, fill = Temperature), position = "dodge", alpha = 0.25)+
  geom_point()+
  scale_color_manual(values=stress.cols)+
  scale_shape_manual(values=c("PMU1"=16,"HSP26"=2))+
  scale_fill_manual(values = stress.cols)+
  coord_cartesian(ylim=c(0,1))+
  facet_grid(Temperature ~ .)
p_native_Occ


ggsave("../figures/Supplemental/Sucrose_native_Occ.pdf",
        egg::set_panel_size(p=p_native_Occ+labs(x="",y="")+set_label_size+
                              theme(legend.position="none",
                                    strip.text.x = element_blank()),
                            width=unit(30,"mm"),height=unit(30,"mm")),
       width=100,height=100,units="mm",bg = "transparent",dpi=600)
```


```{r}
genes_to_label <- c("HAC1","GCN4")
df_30C_occ <- df_Occ_mean_minfilt %>%
  filter(Treatment%in%c("none","mock"),Temperature=="30C") %>%
  group_by(ORF) %>%
  summarise(Occ.odds.mean = exp(mean(log(Occ.odds.mean))))
df <- df_hairpins %>% full_join(df_30C_occ,by="ORF") %>%
  left_join(gene_labels,by="ORF") %>%
  left_join(df_Weinberg,by="ORF") %>%
  filter(Occ.odds.mean>0) %>%
  mutate(gene_label = if_else(gene%in%genes_to_label,gene,""))
df_corr <- df %>% ungroup %>%
  nest() %>%
  mutate(corr = map(data,function(df){
    df %>% select(ORF,Zsup.mean,TE,Occ.odds.mean,TPM.mean) %>% column_to_rownames(var="ORF") %>% correlate(method="spearman")
  })) %>%
  select(-data) %>%
  unnest(corr) 
p_TPM_Occ <- ggplot(df,
       aes(x=TPM.mean,y=Occ.odds.mean))+
  scale_x_log10nice()+
  scale_y_log10nice()+
  coord_cartesian(xlim=c(1,1e4),ylim=c(0.1,50))+
  geom_point(alpha=0.2, size = 0.3)+
  geom_point(data=df %>% filter(gene%in%genes_to_label),size=2,color="red")+
  geom_text_repel(data=df,size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0)+
  labs(x="mRNA Abundance",y="Rib. Occ.\n(odds)")
p_TPM_Occ

p_Z_box <- ggplot(df,
                  aes(x=1,y=Zsup.mean))+
  geom_hline(yintercept=0,linetype="dotted")+
  geom_point(data=df%>%filter(gene%!in%genes_to_label),position=position_jitter(width=0.43),alpha=0.08, size = 1, shape = 16)+
  #geom_boxplot(fill=NA,outlier.shape=NA)+
  geom_violin(fill=NA)+
  geom_point(data=df%>%filter(gene%in%genes_to_label),alpha=1,color="red",size=3, shape = 16)+
  #geom_text_repel(data=df%>%filter(gene=="GCN4"),size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0,nudge_y=2.5,nudge_x=0.25)+
  #geom_text_repel(data=df%>%filter(gene=="HAC1"),size=4.2,aes(label=gene_label),max.overlaps = 10000,min.segment.length = 0,nudge_y=-2.5 ,nudge_x=0.25)+
  labs(x="",y="zSup (30°C)")+
  theme(axis.title.x=element_blank(),  # Removes x-axis label
        axis.text.x=element_blank(),   # Removes x-axis tick labels
        axis.ticks.x=element_blank(),   # Removes x-axis ticks
        axis.title.y = element_text(margin = margin(t = 0, r = 0, b = 0, l = 0, unit = "pt"))
        )
p_Z_box
p_3B_occ <- plot_grid(p_TPM_Occ,p_Z_box,align="hv",rel_widths=c(1,0.7 ))
p_3B_occ
ggsave("../figures/Supplemental/HAC1_GCN4_Occupancy.pdf",egg::set_panel_size(p=p_TPM_Occ+labs(x="",y=""),width=unit(30,"mm"),height=unit(30,"mm")),
       width=50,height=50,units="mm",bg="transparent",dpi=600)
```

#Figure 6D Relative translation of different depletion strains

```{r}
depletion_translation_data <- read_csv(file.path(github_dir,"data_processed/Fig6/radiolabelled_translation_depletions.csv"))
depletion_translation_data_summary <- read_csv(file.path(github_dir,"data_processed/Fig6/radiolabelled_translation_depletions_summary.csv"))

depletion_translation_plot <- ggplot(data = depletion_translation_data_summary %>% filter(Strain != "yHG031"), aes(x = protein, y = mean_norm)) +
  geom_col(position = "dodge", aes( x = protein, y = mean_norm, fill = protein, alpha = Treatment, color = protein)) +
  geom_errorbar(aes(ymin = mean_norm - sd_norm, ymax = mean_norm + sd_norm, group = Treatment, color = protein), width =0, position = position_dodge(width = 0.9)) +
  geom_point(data = depletion_translation_data %>% filter(Strain != "yHG031"), aes(group = Treatment, x = protein, y = normalized_counts), position = position_dodge(width = 0.9), size = 0.8) +
  ylab("Relative Translation") +
  xlab("Initiation factor") +
  scale_fill_manual(values = c("#F5C710", "#E69F00", "#D55E00", "#999999" ,"#009E73","#0072B2","#56B4E9","#CC79A7"), name = "Depleted protein")+
   scale_color_manual(values = c("#F5C710", "#E69F00", "#D55E00", "#999999" ,"#009E73","#0072B2","#56B4E9","#CC79A7"), name = "Depleted protein")+
  scale_alpha_manual(values = c(0.1, 0.7))+
  guides(color = "none", fill = "none", alpha = "none") 

depletion_translation_plot

ggsave( "../figures/Figure6/deplete_translation_plot.pdf",
       egg::set_panel_size(p=depletion_translation_plot+theme(axis.title = element_blank()),
                           width=unit(80,"mm"),height=unit(50,"mm")),
       width=120,height=110,units="mm",bg = "transparent")

```
#Figure 6E Bem2/PGK1 qPCR-TSP vs radiolabelling translation plot in depletion strains
```{r}
tsp_translation_aid <- read_csv(file.path(github_dir,"data_processed/Fig6/tsp_qpcr_vs_translation.csv"))

deplete_condensation_plot <- ggplot(data = tsp_translation_aid %>% filter(Strain != "BY4741"), aes(x = fc_count_per_od, y = compiled_ave_fc_sp_enrichment, color = protein))+
  scale_loglog2()+
  geom_errorbar(aes(xmin = fc_count_per_od - error_count_per_od, xmax = fc_count_per_od + error_count_per_od), width = 0)+
  geom_errorbar(aes(ymin = compiled_ave_fc_sp_enrichment - compiled_se_fc_sp_enrichment,ymax = compiled_ave_fc_sp_enrichment + compiled_se_fc_sp_enrichment), width = 0)+
    geom_point(size = 2)+
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73", "#F5C710", "#0072B2", "#D55E00", "#CC79A7", "#999999"), name = "Depleted \nprotein", labels = c("eIF3b", "eIF5", "eIF4G", "eIF2α", "eIF4E", "eIF4A", "eIF5B", 'eIF4B'))+
  xlab("Relative translation \n(depletion vs. mock)")+
  ylab("Relative condensation \n(depletion vs. mock)")+
  theme(axis.text = element_text(size = 10),
  		  axis.title = element_text(size = 10), 
  		  legend.title = element_text(size = 10),
  		  legend.text = element_text(size = 10))+
  coord_cartesian(xlim = c(0.05, 1))+
  geom_vline(aes(xintercept = 1), linetype = "dashed")+
    #this is ratio of CHX/30C mock
  geom_vline(aes(xintercept = 0.04882988), linetype = "dashed")

deplete_condensation_plot

ggsave( "../figures/Figure6/deplete_condensation_plot.pdf",
       egg::set_panel_size(p=deplete_condensation_plot+theme(axis.title = element_blank()),
                           width=unit(40,"mm"),height=unit(40,"mm")),
       width=80,height=100,units="mm",bg = "transparent")

```
#Figure S6

#Polysome profiles vs. Relative translation
```{r}

# Define a dataframe with the corrections
corrections <- data.frame(
  old_name = c("yHG55", "yHG38", "yJB42", "yHG72"),
  new_name = c("yHG055", "yHG038", "yJB042", "yHG072")
)

polysome_ratio<- read_csv(file.path(github_dir,"data_processed/Fig6/polysome_monsome_master.csv")) %>% 
  mutate(Strain = if_else(Strain %in% corrections$old_name, 
                          corrections$new_name[match(Strain, corrections$old_name)], 
                          Strain)) 

polysome_ratio_mean <- polysome_ratio %>%
  pivot_wider(names_from = Treatment, values_from = PM_ratio) %>%
  group_by(Strain, Rep) %>% 
  summarise(mock_PM_ratio = max(mock, na.rm = TRUE),
            treat_PM_ratio = max(treat, na.rm = TRUE)) %>% 
  #filter(!(Strain == "yJB147" & Rep == "rep2")) %>% 
  mutate(PM_ratio_fc = treat_PM_ratio/mock_PM_ratio) %>% group_by(Strain) %>% summarise(mean_PM_ratio_fc = mean(PM_ratio_fc), sd_PM_ratio_fc = sd(PM_ratio_fc))

rad_translation_ratio <- read_csv(file.path(github_dir,"data_processed/Fig6/radiolabelled_translation_ratio.csv"))

polysome_radioactive_compare <- polysome_ratio_mean %>% left_join(rad_translation_ratio, by = "Strain") %>% filter(!is.na(fc_count_per_od)) %>% mutate(protein = 
                      case_when(Strain == "yHG055"~ "eIF4B",
                               Strain == "yJB147" ~"eIF5",
                               Strain == "yJB148" ~"eIF5b", 
                               Strain == "yJB042" ~'eIF3b',
                               Strain == "yHG038" ~ 'eIF4E',
                               Strain == "yHG031" ~"eIF4G1", 
                               Strain == "yHG072" ~ "eIF4A1(A2ko)",
                              Strain == "yJB143" ~ "eIF2alpha",
                              Strain == "yJB262" ~ "eIF4G1(G2ko)")) %>% 
  mutate(protein = factor(protein, levels = c('eIF3b',"eIF5","eIF4G1(G2ko)","eIF2alpha",'eIF4E', 'eIF4A1(A2ko)','eIF5b','eIF4B')))

translation_compare<- ggplot(data = polysome_radioactive_compare, aes(x = mean_PM_ratio_fc, y = fc_count_per_od, color = protein))+
  geom_point(size = 2.5)+
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73", "#F5C710", "#0072B2", "#D55E00", "#CC79A7", "#999999"), name = "Depleted protein")+
  geom_errorbar(aes(ymin = fc_count_per_od - error_count_per_od, ymax = fc_count_per_od + error_count_per_od))+
  geom_errorbar(aes(xmin=mean_PM_ratio_fc -sd_PM_ratio_fc , 
                     xmax=mean_PM_ratio_fc +sd_PM_ratio_fc ))+
  xlab("Polysome/Monosome ratio \nfold difference (Treat vs Mock)")+
  ylab("Radioactivity Counts \nfold difference (Treat vs Mock)")

translation_compare

translation_compare_plot <- translation_compare +theme(legend.position = "none", axis.text =element_text(size = 10), aspect.ratio = 1, axis.title = element_blank())

translation_compare_plot 


ggsave("../figures/Supplemental/S6/polysome_radioactive_compare.pdf", translation_compare_plot, width = 1.75, height = 1.75)
```

Relative translation vs. relative depletion
```{r}
WB_data <- read_csv(file.path(github_dir,"data_processed/Fig6/WB_data_0904023.csv"))
translation_ratio <- read_csv(file.path(github_dir,"data_processed/Fig6/radiolabelled_translation_ratio.csv"))

compare_WB <- left_join(translation_ratio,WB_data , by = "Strain") %>% 
  mutate(Protein = factor(Protein, levels = c('eIF3b',"eIF5","eIF4G","eIF2a",'eIF4E', 'eIF4A','eIF5b','eIF4B'))) 

compare_WB_translation <- ggplot(data = compare_WB %>% filter(Strain != "BY4741"), aes(x = mean_protein_remaining/100, y = fc_count_per_od, color = Protein))+
  geom_point(size = 2)+
  geom_errorbar(aes(xmin= mean_protein_remaining/100 - sd/100, xmax = mean_protein_remaining/100 + sd/100))+
   geom_errorbar(aes(ymin = fc_count_per_od - error_count_per_od, ymax = fc_count_per_od + error_count_per_od), width  = 0.01)+
  scale_color_manual(values = c("#E69F00", "#56B4E9", "#009E73", "#F5C710", "#0072B2", "#D55E00", "#CC79A7", "#999999"), name = "Depleted protein")+
  ylab("Relative translation \n(Treat/Mock)")+
  xlab("Fraction protein remaining \nafter depletion ")+
 # ylim(0, 1)+
  xlim(c(0, 0.2))+
    scale_x_continuous(breaks = c(0, 0.1, 0.2))+
  theme(axis.text = element_text(size = 10),
  		  #axis.title = element_text(size = 10), 
  		  #legend.title = element_text(size = 20),
  		  #legend.text = element_text(size = 16), 
  		  legend.position = "none", aspect.ratio = 1, axis.title = element_blank())

compare_WB_translation

ggsave( "../figures/Supplemental/S6/compare_WB_translation.pdf", compare_WB_translation, width = 1.75, height = 1.75)
```
Relative translation decreases during heat shock measured via radiolabelling
```{r}

temp_translation_data <- read_csv(file.path(github_dir,"data_processed/Fig6/temp_translation_data.csv"))

temp_translation_plot <- ggplot(data = temp_translation_data, aes(x = Treatment, y = fc_count_per_od, color = Treatment))+
  geom_point(size = 2)+
  geom_errorbar(aes(x =Treatment, ymin = fc_count_per_od + error_count_per_od, ymax = fc_count_per_od - error_count_per_od), width = 0.1)+
  ylab("Relative Translation \nto 30°C")+
  xlab("Treatment (15 min)")+
  scale_color_manual(values = c("30C"="#7F7F7F",
                  "42C"=RColorBrewer::brewer.pal(n=7,"Oranges")[4],
                  "46C"=RColorBrewer::brewer.pal(n=7,"Oranges")[6],"CHX" = "black"))+
    theme(axis.text  = element_text(size = 10), aspect.ratio = 1, axis.title = element_blank(), legend.position = "none")

temp_translation_plot 

ggsave( "../figures/Supplemental/S6/temp_translation_plot.pdf", temp_translation_plot, width = 1.75, height = 1.75)
```
#Polysome traces 

```{r}
# Define the read_and_plot function
plot_polysome <- function(file_path, offsets, scale_color_manual_values, protein_name) {
  # Read data from the exported CSV file
  data <- read.csv(file.path(github_dir, file_path), stringsAsFactors = FALSE)
  

  # Rename "Distance.mm." column to "Distance" if needed
  if ("Distance.mm." %in% colnames(data)) {
    data <- data %>% rename(Distance = `Distance.mm.`)
  }
  
  # Calculate adjusted Distance and Absorbance
  data <- data %>%
    mutate(Distance.adj = Distance - offsets[1],  # Assuming only one offset for simplicity
           Absorbance.adj = Absorbance - 0.003,
           Absorbance.norm = Absorbance.adj / sum(Absorbance.adj, na.rm = TRUE))
  
  # Filter data
  data <- data %>%
    filter(Distance.adj > 12, Distance.adj < 95)
  
  # Create ggplot with facet_wrap
  plot <- ggplot(data, aes(x = Distance.adj, y = Absorbance.norm, color = Treatment)) +
    geom_line(size = 0.75) +
    xlab("Distance (a.u)") +
    ylab("A254nm (a.u)") +
    theme(axis.text.x = element_blank(),
          axis.text.y = element_blank()) +
    scale_color_manual(values = scale_color_manual_values) +
    facet_wrap(vars(Rep)) +
    guides(color = FALSE)+
    ggtitle(paste("Protein:", protein_name))
  
  return(list(plot = plot, data = data))
}
```

```{r}

file_path <- "data_processed/Fig6/polysomes/yJB143_eIF2alpha_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#F5C710")  # Modify with your color values
protein_name <- "eIF2α"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF2alpha_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yJB42_eIF3b_polysome_profile.csv"
offsets <- c(1, 50, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#E69F00")  # Modify with your color values
protein_name <- "eIF3b"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF3b_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yHG72_eIF4A_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#D55E00")  # Modify with your color values
protein_name <- "eIF4A"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF4A_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yHG55_eIF4B_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#999999")  # Modify with your color values
protein_name <- "eIF4B"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave("../figures/Supplemental/S6/eIF4B_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yHG38_eIF4E_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#0072B2")  # Modify with your color values
protein_name <- "eIF4E"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF4E_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yJB262_eIF4G_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#009E73")  # Modify with your color values
protein_name <- "eIF4G"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF4G_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yJB147_eIF5_polysome_profile.csv"
offsets <- c(-5, 0.25, -1, -3.5)  # Modify with your offsets
scale_color_manual_values <- c("black", "#56B4E9")  # Modify with your color values
protein_name <- "eIF5"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF5_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)

file_path <- "data_processed/Fig6/polysomes/yJB148_eIF5B_polysome_profile.csv"
offsets <- c(1, 0, 0, 0)  # Modify with your offsets
scale_color_manual_values <- c("black", "#CC79A7")  # Modify with your color values
protein_name <- "eIF5B"  # Modify with your protein name
result <- plot_polysome (file_path, offsets, scale_color_manual_values, protein_name)
result$plot

ggsave( "../figures/Supplemental/S6/eIF5B_profile.pdf", result$plot+theme(strip.text.x= element_blank(), plot.title = element_blank()), width =3, height = 2)
```